### 2015-04-12 src/ArticleReadyTableGenerate-c.tex
Script to run pairwise comparisons between 5 diag subclasses

\documentclass[12pt]{article}

\usepackage{listings}
\usepackage{pgfplots}
\usepackage{pgfplotstable}
%\pgfplotsset{compat=1.10}
\usepackage[hang,footnotesize,bf,margin=.5in]{caption}
\usepackage{epstopdf}
\usepackage[indention=10pt,singlelinecheck=false]{subfig}
\usepackage{float}
\usepackage{graphicx}
\usepackage{rotating}
\usepackage[top=1in, bottom=1.3in, left=.7in, right=.7in, paperwidth=8.5in, paperheight=11in]{geometry}
\usepackage{setspace}
\usepackage{multirow}
\usepackage{array}
\usepackage{pdfpages}
\usepackage[style=numeric,url=false,isbn=false,doi=false,maxnames=30,natbib=true, uniquename=init,firstinits]{biblatex}
\AtEveryBibitem{%
  \clearfield{day}%
  \clearfield{month}%
  \clearfield{endday}%
  \clearfield{endmonth}%
}
\DeclareNameAlias{default}{last-first}
\renewbibmacro{in:}{}
\setlength{\footskip}{24pt}
\newcommand{\hilight}[1]{\colorbox{yellow}{#1}}
\newcommand\T{\rule{0pt}{2.6ex}}
\newcommand\B{\rule[-1.2ex]{0pt}{0pt}}
\usepackage{tikz}
\usetikzlibrary{positioning,shapes,arrows}

\bibliography{library,library_added}

\begin{document}
%\SweaveOpts{concordance=TRUE}

\begin{table}[t]
  \centering
	\begin{tabular}{rrrrrrr}
		\hline
		Diag \T& Gender & Number & \multicolumn{2}{c}{Age (Yrs)} & \multicolumn{2}{c}{YrsEd (Yrs)} \\
		& \B & & Mean & SD & Mean & SD \\ \hline
% latex table generated in R 3.1.2 by xtable 1.7-4 package
% Tue Dec  2 14:59:07 2014
  \hline
normal & Male & 225 & 78.41 & 4.70 & 12.49 & 3.78 \\ 
  normal & Female & 328 & 78.67 & 4.91 & 11.09 & 3.03 \\ 
  aMCI & Male &  58 & 79.18 & 4.69 & 12.71 & 4.00 \\ 
  aMCI & Female &  45 & 80.44 & 5.22 & 11.27 & 3.19 \\ 
  nMCI & Male &  45 & 78.09 & 4.00 & 11.82 & 3.92 \\ 
  nMCI & Female &  77 & 79.34 & 4.69 & 10.67 & 3.15 \\ 
  amdMCI & Male &  45 & 79.12 & 5.16 & 12.28 & 3.82 \\ 
  amdMCI & Female &  37 & 78.73 & 4.63 & 11.01 & 2.93 \\ 
  nmdMCI & Male &   9 & 76.87 & 2.69 & 13.00 & 5.50 \\ 
  nmdMCI & Female &  17 & 75.83 & 3.38 & 9.88 & 2.39 \\ 
   \hline

	\end{tabular}
	\caption{\textbf{Summary of data used for MCI analysis}.  Summary statistics on the number, age, and years of education of individuals used for the analysis.  Data broken down based on gender and diagnosis.}
	\label{wave1data}
\end{table}

### 2015-04-12 src/TablesKnitr.tex
Script to run pairwise comparisons between 5 diag subclasses

\documentclass[11pt]{article}\usepackage[]{graphicx}\usepackage[]{color}
%% maxwidth is the original width if it is less than linewidth
%% otherwise use linewidth (to make sure the graphics do not exceed the margin)
\makeatletter
\def\maxwidth{ %
  \ifdim\Gin@nat@width>\linewidth
    \linewidth
  \else
    \Gin@nat@width
  \fi
}
\makeatother

\definecolor{fgcolor}{rgb}{0.345, 0.345, 0.345}
\newcommand{\hlnum}[1]{\textcolor[rgb]{0.686,0.059,0.569}{#1}}%
\newcommand{\hlstr}[1]{\textcolor[rgb]{0.192,0.494,0.8}{#1}}%
\newcommand{\hlcom}[1]{\textcolor[rgb]{0.678,0.584,0.686}{\textit{#1}}}%
\newcommand{\hlopt}[1]{\textcolor[rgb]{0,0,0}{#1}}%
\newcommand{\hlstd}[1]{\textcolor[rgb]{0.345,0.345,0.345}{#1}}%
\newcommand{\hlkwa}[1]{\textcolor[rgb]{0.161,0.373,0.58}{\textbf{#1}}}%
\newcommand{\hlkwb}[1]{\textcolor[rgb]{0.69,0.353,0.396}{#1}}%
\newcommand{\hlkwc}[1]{\textcolor[rgb]{0.333,0.667,0.333}{#1}}%
\newcommand{\hlkwd}[1]{\textcolor[rgb]{0.737,0.353,0.396}{\textbf{#1}}}%

\usepackage{framed}
\makeatletter
\newenvironment{kframe}{%
 \def\at@end@of@kframe{}%
 \ifinner\ifhmode%
  \def\at@end@of@kframe{\end{minipage}}%
  \begin{minipage}{\columnwidth}%
 \fi\fi%
 \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
 \colorbox{shadecolor}{##1}\hskip-\fboxsep
     % There is no \\@totalrightmargin, so:
     \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
 \MakeFramed {\advance\hsize-\width
   \@totalleftmargin\z@ \linewidth\hsize
   \@setminipage}}%
 {\par\unskip\endMakeFramed%
 \at@end@of@kframe}
\makeatother

\definecolor{shadecolor}{rgb}{.97, .97, .97}
\definecolor{messagecolor}{rgb}{0, 0, 0}
\definecolor{warningcolor}{rgb}{1, 0, 1}
\definecolor{errorcolor}{rgb}{1, 0, 0}
\newenvironment{knitrout}{}{} % an empty environment to be redefined in TeX

\usepackage{alltt}
\usepackage[margin=1in]{geometry}   % set up margins
\usepackage{enumerate}              % fancy enumerate
\usepackage{amsmath}                % used for \eqref{} in this document
\usepackage{verbatim}               % useful for \begin{comment} and \end{comment}
\usepackage{comment}
\usepackage[pdftitle={Homework With knitr}, colorlinks=true, linkcolor=blue,
citecolor=blue, urlcolor=blue, linktocpage=true, breaklinks=true]{hyperref}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\begin{document}
%%%%%%%%%%%%%%%%   Sweave Options  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\SweaveOpts{fig.path='./Graphs/alan-', comment=NA, prompt=FALSE}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{Tables with \textbf{xtable} and \textbf{knitr}}
\author{Alan T. Arnholt\\ STT 3851}
\date{Spring 2012}
\maketitle

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}

{\ttfamily\noindent\color{warningcolor}{\#\# Warning in library(package, lib.loc = lib.loc, character.only = TRUE, logical.return = TRUE, : there is no package called 'PASWR'}}\end{kframe}
\end{knitrout}

Here are a few examples using the function \texttt{xtable()} form the \textbf{R} package \texttt{xtable} I used to generate \LaTeX{} code for tabular output without manually entering the values in a tabular environment. To get beyond the basic examples in this document, read the documentation and customize until you are happy.  Consider a table created with \texttt{xtabs()}.

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{T1} \hlkwb{<-} \hlkwd{xtabs}\hlstd{(}\hlopt{~} \hlstd{Ease} \hlopt{+} \hlstd{Treatment,} \hlkwc{data} \hlstd{= EPIDURALf)}
\end{alltt}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in terms.formula(formula, data = data): object 'EPIDURALf' not found}}\begin{alltt}
\hlstd{T1}
\end{alltt}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in eval(expr, envir, enclos): object 'T1' not found}}\end{kframe}
\end{knitrout}

Now we want this to appear in a ``pretty'' format.

\begin{kframe}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in xtable(T1): object 'T1' not found}}\end{kframe}

Creating a caption with \texttt{xtable()} for Table \ref{MyT1}.
\begin{kframe}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in xtable(T1, caption = "{}Table of Something"{}, label = "{}MyT1"{}): object 'T1' not found}}\end{kframe}

Consider the regression results below and those shown in Tables \ref{RR} and \ref{RR2}.

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{mod} \hlkwb{<-} \hlkwd{lm}\hlstd{(gpa} \hlopt{~} \hlstd{sat,} \hlkwc{data} \hlstd{= Grades)}
\end{alltt}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in is.data.frame(data): object 'Grades' not found}}\begin{alltt}
\hlstd{SR} \hlkwb{<-} \hlkwd{summary}\hlstd{(mod)}\hlopt{$}\hlstd{coefficients}
\end{alltt}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in summary(mod): object 'mod' not found}}\begin{alltt}
\hlstd{SR}
\end{alltt}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in eval(expr, envir, enclos): object 'SR' not found}}\begin{alltt}
\hlstd{AR} \hlkwb{<-} \hlkwd{anova}\hlstd{(mod)}
\end{alltt}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in anova(mod): object 'mod' not found}}\begin{alltt}
\hlstd{AR}
\end{alltt}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in eval(expr, envir, enclos): object 'AR' not found}}\end{kframe}
\end{knitrout}

\begin{kframe}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in xtable(SR, caption = "{}Regression results"{}, label = "{}RR"{}): object 'SR' not found}}\end{kframe}

\begin{kframe}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in xtable(SR, caption = "{}Regression results with 4 digits"{}, label = "{}RR2"{}, : object 'SR' not found}}\end{kframe}

\begin{kframe}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in xtable(AR, caption = "{}ANOVA"{}, label = "{}AR"{}): object 'AR' not found}}\end{kframe}

Suppose you want the label \texttt{Pr(>F)} in Table \ref{AR} to read $\wp$-value.

\begin{kframe}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in colnames(AR) <- c("{}DOF"{}, "{}Sum Sq"{}, "{}Mean Sq"{}, "{}F value"{}, "{}\$\textbackslash{}\textbackslash{}wp\$-value"{}): object 'AR' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in xtable(AR, caption = "{}ANOVA with \$\textbackslash{}\textbackslash{}wp\$-value changed"{}, label = "{}ARpvalue"{}): object 'AR' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in print(AR, sanitize.text.function = function(x) \{: object 'AR' not found}}\end{kframe}

\end{document}

### 2015-04-12 src/LCDM_pooled_5_class_pairwise_compare.R

@@ -1,0 +1,128 @@
+
+
+
+LCDM_analysis <- function(fileNames,condTests,REGION, pairs.to.compare,
+                 analysis.tag,group.names){
+  ### Pre-Processing 
+  require(MASS)
+  num.groups <- length(group.names)
+  b<-list(); dists<-c(); distsl<-c();
+  for (i in 1:length(fileNames)){ 
+    distsl[i]<-read.table(fileNames[i])
+    distsl[[i]]=distsl[[i]][distsl[[i]]>-2] 
+    distsl[[i]]=distsl[[i]][distsl[[i]]<8] 
+  }
+  minlength=min(as.numeric(lapply(distsl,length)))
+  dists=sapply(distsl,sample,minlength) #for tests requiring same number in group
+  
+  ######### Simple Summary Statistics ########
+  
+  subdir.name <- paste0("test_results_",analysis.tag )
+  if (!(subdir.name %in% list.dirs()))  (dir.create(subdir.name))
+  pdf(file=paste(subdir.name,"/summarystat_",REGION,".pdf",sep=''))
+  
+  col= rainbow(num.groups)
+  thk95<-c()
+  thk99<-c()
+  vol95<-c()
+  vol99<-c()
+  for(i in 1:length(fileNames)){ 
+    if (i==1) 
+      hist(distsl[[i]], 100, freq=FALSE, col="white", border="white", xlim=c(-4,10), ylim=c(0,.4),main=NA,xlab="Distance (mm)",ylab="Probability Density")
+    par(new=T);
+    dens1=density(distsl[[i]])
+    lines(dens1, lwd=1, col=col[i])
+    thk95[i]=quantile(distsl[[i]],.95)
+    thk99[i]=quantile(distsl[[i]],.99)
+  }
+  legend(6, .3, paste(group.names), cex=1,  col= col,lwd=2, bty="n");
+  
+  for(i in 1:length(fileNames)){ 
+    cdf1=ecdf(round(distsl[[i]],3))
+    if (i==1) 
+    {
+      plot(cdf1, verticals=TRUE, xlim=c(-2,7),do.points=F, lwd=.5, col=col[i], main=NA,xlab="Distance (mm)", ylab="Cumulative Probability Density")
+      par(new=T);
+    }		
+    else { lines(cdf1, lwd=.5, col=col[i]) }
+  }
[…]

### 2016-02-27 src/pool_LCDM_stats.py
Python script to replace bash script that pools LCDM values

@@ -1,0 +1,66 @@
+#! /usr/bin/env python
+__author__ = 'Sancar'
+import os
+import os.path.join as join_p
+import glob
+
+
+
+
+regions= ['cingulate','TL']
+
+subregions={'TL':['stg','mtg','itg'], 'cingulate':[ 'postcing', 'antcing']}
+
+
+diags=[
+    'normal',
+#    normal_m
+#    normal_f
+    'aMCI',
+    'amdMCI',
+#    amnesticMCI_m
+#    amnesticMCI_f
+    'nMCI',
+    'nmdMCI'
+#    nonamnesticMCI_m
+#    nonamnesticMCI_f
+
+#    normtest1_aMCI
+#    normtest2_aMCI
+]
+
+hemis=['rh','lh']
+
+wave1_dir1 = '/cis/project/sydney/data_fslcdm/MAS.20100921_Antsy/'
+wave1_dir2 = "/cis/project/sydney/data_fslcdm/MAS.20110324_Antsy/'
+for region in regions:
+    region_name = hemi+'_'+region
+    for hemi in hemis:
+        for diag in diags:
+            idfile='ids_5_subclass/Diag_'+diag+'_ID_list.csv' #wave1_${diag}_used.txt'
+            id_fh = open(idfile,'r')
+            ids = id_fh.readlines()
+            for id in ids:
+
+                for sub in subregions[region]:
+                    sub_region=hemi+'_'+sub
+                    output_fname = '/cis/home/sadali/pooled_analysis/pooled_5subclass_antsy_files_used/'+sub_region+'_'+diag+'_wave1_pooled_antsy.txt'
+                    #of_handle = open (output_fname,'a')
+
+                    for id in ids:
+                        id = id.strip()
+                    #   full_dir_names = os.listdir(wave1_dir1)
+                    #   full_path =  os.path.join(wave1_dir1, x for x in full_dir_names if x.startswith(id), 'FSLCDM_v2.3',region_name,sub_region+'_1_manseg_quartile_pialmsk_AntsyGrey.txt')
+                        full_path =  os.path.join(wave1_dir1, id+"*", 'FSLCDM_v2.3',region_name,sub_region+'_1_manseg_quartile_pialmsk_AntsyGrey.txt')
+                        f = glob.glob(full_path):
+
+                        if os.path.exists(f) and os.isfile(f) and os.path.getsize(f)>0:
+                            os.system("cat "+f+" >> "+output_fname)
+                        else:
[…]

### 2016-02-27 src/pool_LCDM_stats.py
fix syntax errors of pool python script

@@ -1,10 +1,10 @@
-#! /usr/bin/env python
+#! /usr/bin/python
 __author__ = 'Sancar'
 import os
-import os.path.join as join_p
+from  os.path import join as join_p
 import glob
 
-
+ROOT = "/cis/home/sadali/MAS_score_analysis/"
 
 
 regions= ['cingulate','TL']
@@ -32,19 +32,23 @@ diags=[
 hemis=['rh','lh']
 
 wave1_dir1 = '/cis/project/sydney/data_fslcdm/MAS.20100921_Antsy/'
-wave1_dir2 = "/cis/project/sydney/data_fslcdm/MAS.20110324_Antsy/'
+wave1_dir2 = '/cis/project/sydney/data_fslcdm/MAS.20110324_Antsy/'
 for region in regions:
-    region_name = hemi+'_'+region
+
     for hemi in hemis:
+        region_name = hemi+'_'+region
         for diag in diags:
-            idfile='ids_5_subclass/Diag_'+diag+'_ID_list.csv' #wave1_${diag}_used.txt'
+            idfile=join_p(ROOT,'data','ids_5_subclass','Diag_'+diag+'_ID_list.csv' ) #wave1_${diag}_used.txt'
             id_fh = open(idfile,'r')
             ids = id_fh.readlines()
             for id in ids:
 
                 for sub in subregions[region]:
                     sub_region=hemi+'_'+sub
-                    output_fname = '/cis/home/sadali/pooled_analysis/pooled_5subclass_antsy_files_used/'+sub_region+'_'+diag+'_wave1_pooled_antsy.txt'
+                    output_dir = join_p(ROOT,'data','pooled_analysis','pooled_5subclass_antsy_files_used')
+                    if not os.path.exists(output_dir):
+                        os.makedirs(output_dir)
+                    output_fname = join_p(output_dir,sub_region+'_'+diag+'_wave1_pooled_antsy.txt')
                     #of_handle = open (output_fname,'a')
 
                     for id in ids:
@@ -52,7 +56,7 @@ for region in regions:
                     #   full_dir_names = os.listdir(wave1_dir1)
                     #   full_path =  os.path.join(wave1_dir1, x for x in full_dir_names if x.startswith(id), 'FSLCDM_v2.3',region_name,sub_region+'_1_manseg_quartile_pialmsk_AntsyGrey.txt')
[…]

### 2016-02-27 src/pool_LCDM_stats.py
Fixed. running to get pooled data files

@@ -53,18 +53,29 @@ for region in regions:
 
                     for id in ids:
                         id = id.strip()
-                    #   full_dir_names = os.listdir(wave1_dir1)
+                        full_dir_names = os.listdir(wave1_dir1)
                     #   full_path =  os.path.join(wave1_dir1, x for x in full_dir_names if x.startswith(id), 'FSLCDM_v2.3',region_name,sub_region+'_1_manseg_quartile_pialmsk_AntsyGrey.txt')
                         full_path =  os.path.join(wave1_dir1, id+"*", 'FSLCDM_v2.3',region_name,sub_region+'_1_manseg_quartile_pialmsk_AntsyGrey.txt')
-                        f = glob.glob(full_path)
+                        print full_path
+                        f = glob.glob(str(full_path))
+                        print "file matches for "+id
 
-                        if os.path.exists(f) and os.isfile(f) and os.path.getsize(f)>0:
-                            os.system("cat "+f+" >> "+output_fname)
+                        for file_match in f:
+                          print file_match
+
+                        if  len(f) > 0 and os.path.exists(f[0]) and os.path.isfile(f[0]) and os.path.getsize(f[0])>0:
+                            os.system("cat "+f[0]+" >> "+output_fname)
                         else:
+
                             full_path =  os.path.join(wave1_dir2, id+"*", 'FSLCDM_v2.3', region_name, sub_region+'_1_manseg_quartile_pialmsk_AntsyGrey.txt')
-                            f = glob.glob(full_path)
-                            if os.path.exists(f) and os.isfile(f) and os.path.getsize(f)>0:
-                                os.system("cat "+f+" >> "+output_fname)
+
+                            f = glob.glob(str(full_path))
+                            print "file matches for "+id
+
+                            for file_match in f:
+                              print file_match
+                            if len(f) > 0  and os.path.exists(f[0]) and os.path.isfile(f[0]) and os.path.getsize(f[0])>0:
+                                os.system("cat "+f[0]+" >> "+output_fname)
 
 
                         print id+" added to pooled stats"

### 2016-02-29 src/ArticleReadyTableGenerate.Rnw
Fix pooling python script. add the Sweave document

\documentclass[12pt]{article}

\usepackage{listings}
\usepackage{pgfplots}
\usepackage{pgfplotstable}
%\pgfplotsset{compat=1.10}
\usepackage[hang,footnotesize,bf,margin=.5in]{caption}
\usepackage{epstopdf}
\usepackage[indention=10pt,singlelinecheck=false]{subfig}
\usepackage{float}
\usepackage{graphicx}
\usepackage{rotating}
\usepackage[top=1in, bottom=1.3in, left=.7in, right=.7in, paperwidth=8.5in, paperheight=11in]{geometry}
\usepackage{setspace}
\usepackage{multirow}
\usepackage{array}
\usepackage{pdfpages}
\usepackage[style=numeric,url=false,isbn=false,doi=false,maxnames=30,natbib=true, uniquename=init,firstinits]{biblatex}
\AtEveryBibitem{%
  \clearfield{day}%
  \clearfield{month}%
  \clearfield{endday}%
  \clearfield{endmonth}%
}
\DeclareNameAlias{default}{last-first}
\renewbibmacro{in:}{}
\setlength{\footskip}{24pt}
\newcommand{\hilight}[1]{\colorbox{yellow}{#1}}
\newcommand\T{\rule{0pt}{2.6ex}}
\newcommand\B{\rule[-1.2ex]{0pt}{0pt}}
\usepackage{tikz}
\usetikzlibrary{positioning,shapes,arrows}

\bibliography{library,library_added}

\begin{document}

%\SweaveOpts{concordance=TRUE}

<<LoadData_and_BasicDataMunge,echo=FALSE,results='hide',warning=FALSE, message=FALSE>>=
# Load Data
library(foreign)
library(dplyr)
library(xtable)
HOME_DIR <- Sys.getenv("HOME")
print(HOME_DIR)
setwd(HOME_DIR)
setwd("./projects/MAS_Score_Analysis")
#setwd( paste0(Sys.getenv("HOME"),"/projects/MAS_Score_Analysis/"))
#The script gets data from  SPSS files, merges data frames to one data frame
source("./src/MAS_MCIsubtype_analysis.R")
all.df<- droplevels(all.df)

all.var.names<- names(all.df)
all.var.names[all.var.names=="W1_subclass"] <- "Diag"
all.var.names[all.var.names=="W1_Ed_year"] <- "YrsEd"
names(all.df)<- all.var.names
all.df$Wave1 <- !is.na(all.df$ICV_W1)
grouping_gender_diag <- group_by(all.df[all.df$Wave1, ], Diag,sex)
print (paste0(sum(all.df$Wave1), "  patients summarized"))
# create a table of summary statistics
summary_table_1.df  <- summarize (grouping_gender_diag, Number= n(), mean_age=mean(age,na.rm=T), sd_age=sd(age,na.rm=T), 
           mean_ed_dur =mean(YrsEd,na.rm=T), sd_ed_dur= sd(YrsEd,na.rm=T) )
summary_table_1.df <- arrange(summary_table_1.df,Diag,sex)

@

\begin{table}[t]
  \centering
	\begin{tabular}{rrrrrrr}
		\hline
		Diag \T& Gender & Number & \multicolumn{2}{c}{Age (Yrs)} & \multicolumn{2}{c}{YrsEd (Yrs)} \\
		& \B & & Mean & SD & Mean & SD \\ \hline
<<Table_1_summarystats, results='asis', eval=TRUE,echo=FALSE>>=
  class(summary_table_1.df)<-"data.frame"
  table.out <- xtable(summary_table_1.df)
  print.xtable(table.out, only.contents=TRUE, include.rownames=FALSE,include.colnames=FALSE)
  @

	\end{tabular}
	\caption{\textbf{Summary of data used for MCI analysis}.  Summary statistics on the number, age, and years of education of individuals used for the analysis.  Data broken down based on gender and diagnosis.}
	\label{wave1data}
\end{table}

<<diag.plot.ICV_1,fig.show='hide',results='asis',echo=FALSE>>=
#Gender, age, ICV, ED.year, hemisphere
library(ggplot2)
library(reshape2)
# Convert all.df to long format
#
all.df.lf<- melt(all.df[all.df$Wave1,], id.var=c(1,2,8,9,10,71),
                 measure.vars=11:40, value.name="LCDM.measure",variable.name="hemi.region.subregion.meas")

num.records <- nrow(all.df.lf)
all.df.lf$hemi <- substr(all.df.lf$hemi.region.subregion.meas,1,2)

all.df.lf$lcdm.stat.string <- strsplit(as.character(all.df.lf$hemi.region.subregion.meas),split="_")
all.df.lf$region <-rep("",num.records)
all.df.lf$aggstat <-rep("",num.records)

for (i in 1:num.records){
  all.df.lf$region[i] <-all.df.lf$lcdm.stat.string[[i]][2]
  all.df.lf$aggstat[i] <-all.df.lf$lcdm.stat.string[[i]][3]

}
agg.stats.names <- unique(all.df.lf$aggstat)

  fig.1<-qplot(data=all.df.lf[all.df$Wave1,],x=ICV_W1,y=LCDM.measure,color=hemi.region.subregion.meas)+facet_grid(aggstat~hemi,scales="free")

print(fig.1)

# plotting  LCDM statistic vs ICV for each statistic (thickness, surface area, volume) for each region/subregion, we ge a plot that shows there does not seem to be significantly positive slope for any of the measures and the conditional correlation between ICV and the measure (given the class) is weak. 
#TODO :   condition  on the class label here.
@

<<ICVStats,eval=TRUE,error=TRUE,echo=FALSE>>=
require(car)
aov.fit<- lm(ICV_W1~YrsEd+age+sex+Diag,data=all.df)
aov.result.type3 <- Anova(aov.fit,type="III")
aov.result <- aov(aov.fit)
# Does ICV show a trend level  group difference (Is p-value for Diag sig?)
print("ICVStats ANOVA with covars")
print(aov.result.type3)

# Does ICV show a trend level  group difference (Is p-value for Diag sig?)
print("ICVStats ANOVA")
print(aov.result)

# Result shows Diag is not significant and can be not included in the rest of the analysis
@

<<ICVStats_plot,  eval=TRUE,echo=FALSE>>=
summary_table_2.df  <- summarize (grouping_gender_diag, mean_ICV=mean(ICV_W1,na.rm=T), sd_ICV=sd(ICV_W1,na.rm=T))

summary_table_2.df.m <- filter(summary_table_2.df,sex=="Male")
summary_table_2.df.f <- filter(summary_table_2.df,sex=="Female")
print.table.df <- select(summary_table_2.df.m,Diag,mean_ICV,sd_ICV)
class(print.table.df) <- "data.frame"
print.table2.df<-select(summary_table_2.df.f,Diag,mean_ICV,sd_ICV)
class(print.table2.df) <- "data.frame"

aov.result.summary <- summary(aov.result)
if (!is.data.frame(aov.result.summary)){
aov.result.summary  <- aov.result.summary[[1]]
}
print(table.out, include.rownames=FALSE,include.colnames=TRUE)

p_vals <- formatC(aov.result.summary$`Pr(>F)` [1:3], digits = 3,drop0trailing=TRUE)
print (aov.result.summary)
Covariate_names <- rownames(aov.result.summary)[1:3]
print(str(aov.result.summary))
print(Covariate_names)
cov_column <- paste(Covariate_names,"(p = ",p_vals,")",sep="")
cov_column <- c(cov_column,rep("",2))
cov_column_2 <-c ("", paste("p = ",aov.result.summary$`Pr(>F)` [4],")",sep=""),"")
cov_column_2 <- c(cov_column_2,rep("",2))

cov_test_cols<-data.frame(Covariate=cov_column,p.value=cov_column_2)
table.out<-xtable(cbind(print.table.df,print.table2.df[,2:3],cov_test_cols))

@

\newpage
\begin{table}[h]
	\centering
	\footnotesize
	\begin{tabular}{rrrrrrrr}
	\hline
	Diag\T & \multicolumn{2}{c}{Male} & \multicolumn{2}{c}{Female} & & &  \\
      	&  Mean & SE                & Mean & SE                  & Covariates & p-value & \\ \hline
<<Table_2_ICV_summarystats, results='asis', eval=TRUE,echo=FALSE>>=
  #class(summary_table_1.df)<-"data.frame"
  #table.out <- xtable(summary_table_1.df)
  print.xtable(table.out, only.contents=TRUE, include.rownames=FALSE,include.colnames=FALSE)
  @
  \end{tabular}
	\caption{\textbf{ICV Statistics}.  ANCOVA results for ICV.}
	\label{Wave1.ICV.stats}
\end{table}

<<subregion_sideway_table_summary_stats,eval=TRUE,echo=FALSE>>=
stat.tables.for.regions <- list()
summ.stats.tables<-list(stg=list(),mtg=list(),itg=list(),postcing=list(),antcing=list())
for (region.for.table in c("stg" ,"mtg","itg","postcing","antcing")){
  all.df.lf.stg    <- filter(all.df.lf, region==region.for.table)

  all.df.lf.stg.lh <- filter(all.df.lf.stg,hemi=="lh")
  all.df.lf.stg.rh <- filter(all.df.lf.stg,hemi=="rh")

  all.df.lf.stg.lh.grp<- group_by(all.df.lf.stg.lh, aggstat, sex,Diag)
  all.df.lf.stg.rh.grp<- group_by(all.df.lf.stg.rh, aggstat, sex,Diag)

  summary_table_3.df.lh  <- summarize (all.df.lf.stg.lh.grp, mean_measure=mean(LCDM.measure,na.rm=T), sd_measure=sd(LCDM.measure,na.rm=T))
  summary_table_3.df.rh  <- summarize (all.df.lf.stg.rh.grp, mean_measure=mean(LCDM.measure,na.rm=T), sd_measure=sd(LCDM.measure,na.rm=T))

  print.table.lh.df <- select(summary_table_3.df.lh ,sex, Diag,mean_measure,sd_measure)
  class(print.table.lh.df) <- "data.frame"

  print.table.rh.df<-select(summary_table_3.df.rh,sex, Diag,mean_measure,sd_measure)
  class(print.table.rh.df) <- "data.frame"

  summ.stats.tables[[region.for.table]] <- list(lh=print.table.lh.df,
                                              rh= print.table.rh.df)

}
print(str(summ.stats.tables))
@

<<ANOVA_Diagnostic_Analysis, echo=FALSE,eval=FALSE>>=

source("./../lib/setupAnova.r")

require(car)
options(contrasts=c("contr.sum", "contr.poly"))
for (region.for.table in c("stg" ,"mtg","itg","postcing","antcing")){
  for (measure.name in agg.stats.names){
print("==============================")
print(paste0("Diagnostics for Subregion = ",region.for.table," ",
             measure.name ))
all.df.lf.stg    <- filter(all.df.lf, region==region.for.table & aggstat==measure.name)
all.df.lf.stg <- setupAnova(all.df.lf.stg)

p.cutoff = 0.05
aov.fit.init <- lm(LCDM.measure~hemi*Diag,data=all.df.lf.stg)
aov.result   <-Anova(aov.fit.init,type="III")

print("hemisphere sig. test")
print(aov.result)

print("both hemis combined ANOVA")
 aov.fit.init<- lm(LCDM.measure~(cYrsEd+cage+sex)*Diag,data=all.df.lf.stg)
      aov.result <-Anova(aov.fit.init,type="III")
print(aov.result)

#print("repeated meas. hemis ANOVA")
#Diagnostic Analysis
 #aov.fit.init<- lm(LCDM.measure~(YrsEd+age+sex+1)*Diag+
#                      Error(hemi/((YrsEd+age+sex)*Diag))
#                    ,data=all.df.lf.stg)
#aov.result <-Anova(aov.fit.init,type="III")
#print(aov.result)

for (sex.var in c( "Male","Female")){
  aov.fit.init.sep.hemi<- lm(LCDM.measure~(cYrsEd+cage)*Diag,data=all.df.lf.stg, subset =  (sex==sex.var))
  aov.result <-Anova(aov.fit.init.sep.hemi,type="III")

  print(paste0("gender: ",sex.var))
  print(aov.result)
}
}
}
@

% For STG, non-significant for SA,vol,thickness 
% in hemi*Diag stat test, 
% combine hemispheres
% sex:Diag interaction is significant for thickness and Vol
% separate based on gender

% For MTG, not significant in hemi*Diag stat test, 
% combine data from hemi

% significant sex:Diag for all Thickness, vol, SA 
%  so  separate female, male

% For ITG,   
% 
% no significance in \textit{hemi:Diag} test, 
% combine hemispheres
% significant sex:Diag in ITG vol
% separate female, male

% For postcing, the interaction  term is significant in hemi*Diag stat test, 
% (separate hemisphere)(only for thickness)
% significant  sex:Diag for postcing vol, so separate female, male

% For antcing,  nonsignificant in hemi*Diag stat test, 
% so combine hemi

% significant hemi:sex:Diag in thickness,volume , so separate female, male

<<ezAnova_tests,echo=FALSE,message=FALSE,eval=FALSE>>=
#print(names(all.df.lf.stg))
#str(all.df.lf.stg$ID)
require(ez)
#ez.anova <- ezANOVA(all.df.lf.stg, dv=.(LCDM.measure), wid=.(ID),
#                    within=.(hemi), between=.(YrsEd,age,sex,Diag))
for (region.for.table in c("stg" ,"mtg","itg","postcing","antcing")){
  for (measure.name in agg.stats.names){

print(paste0("Diagnostics for Subregion = ",region.for.table," ",
             measure.name ))
    all.df.lf.stg    <- filter(all.df.lf, region==region.for.table & aggstat==measure.name)
all.df.lf.stg <- setupAnova(all.df.lf.stg)

ez.anova <- ezANOVA(all.df.lf.stg, dv=.(LCDM.measure), wid=.(ID),
                   within=.(hemi),
         between=.(Diag,sex),between_covariates=.(cage,cYrsEd),
         detailed=TRUE, type=3)
print(ez.anova)
  }
}

@
%ezANOVA  diagnostics (with hemi as repeated measure/within_covariate)
%  STG   Thickness
%  STG   Vol
%  STG    SurfArea
% No Diag:hemi interaction , so combine hemispheres use Hemi as a covariate
% Sex:Diag interaction so separate genders

%  MTG   Thickness
%  MTG   Vol
%  MTG    SurfArea

%  ITG   Thickness
%  ITG   Vol
%  ITG    SurfArea

%  postcing   Thickness   -->  only  one where Diag:hemi interaction is significant . Use separate hemisphere for all postcing
%  postcing   Vol
%  postcing    SurfArea

%  antcing   Thickness
%  antcing   Vol
%  antcing    SurfArea

<<SidewayTable_Creator,echo=FALSE>>=
  #diag.list<-unique(all.df.lf.stg$Diag)
diag.list<-c("normal","aMCI","nMCI","amdMCI","nmdMCI")
for (region.for.table in c("stg" ,"mtg","itg","antcing")){
#  region.for.table="stg"
  print.table.lh.df <- summ.stats.tables[[region.for.table]]$lh 
  print.table.rh.df <-summ.stats.tables[[region.for.table]]$rh

  all.df.lf.stg  <- filter(all.df.lf, region==region.for.table)
  aov.test.results <- data.frame(sex=character(0),aggstat=character(0),Diag=character(0),Covariates=character(0),p_values= numeric(0))

    for (agg.stat.name in agg.stats.names){
      covar.col.all.sex <-c()
      pval.col.all.sex <-c()
      for (sex.var in c( "Male","Female")){

        aov.fit<- lm(LCDM.measure~(YrsEd+age+hemi)*Diag,
                     data=all.df.lf.stg,
                      subset=(sex==sex.var)&(aggstat==agg.stat.name))
        aov.result <- Anova(aov.fit,type=3)

        if (is.data.frame(aov.result)){
        p.vals <- aov.result$`Pr(>F)`
        } else {
          aov.result <- aov.result[[1]]
        p.vals <- aov.result$`Pr(>F)`
        }
        # remove the intercept term regardless of significance
        p.vals[1]<-1
        #the last p.value is always NA
        p.vals[length(p.vals)]<-1

        var.names <- rownames(aov.result)
        var.names <-  gsub(" ","",var.names)
        names(p.vals)<- var.names
        p.value.for.Diag <- p.vals["Diag"]

        p.vals["Diag"] <- 1

        num.sig.vars <- sum(p.vals<p.cutoff)

        if (num.sig.vars>0) {

          sig.var.names <- var.names[p.vals<p.cutoff]
          sig.var.pvals <- p.vals[p.vals<p.cutoff]
          sig.var.pvals <- formatC(sig.var.pvals, digits = 3,drop0trailing=TRUE)
          sig.covar.table.col <- paste(sig.var.names,"(p = ", sig.var.pvals ,")",sep="")          
        }

        covar.col <- rep("",5)
        pval.col <- rep("",5)
        if (num.sig.vars==0) {
          covar.col[1]<- "None"
        } 
        else {
          covar.col[1:num.sig.vars] <- sig.covar.table.col
          covar.col[(num.sig.vars+1):5]<-""
        }
        p.vals <- formatC(p.vals, digits = 3,drop0trailing=TRUE)
        pval.col[1]  <-  formatC(p.value.for.Diag, digits = 3,drop0trailing=TRUE)
        unit.block <- data.frame(sex=sex.var,aggstat=agg.stat.name, Diag=diag.list ,Covariates=covar.col,p_values= pval.col)
        aov.test.results <- rbind(aov.test.results,unit.block)
        covar.col.all.sex <- c(covar.col.all.sex,covar.col)
        pval.col.all.sex  <- c(pval.col.all.sex,pval.col)
      }  
    }
    print(covar.col.all.sex )
    print(pval.col.all.sex )
    print.table.df <- merge(print.table.rh.df,print.table.lh.df,
                        by = c("aggstat","sex","Diag"),sort=FALSE)
    print.table.merged.df<- merge(print.table.df, aov.test.results,
                                    by = c("aggstat","sex","Diag"),
                                  sort=FALSE )

  new.table <- list(print.table.merged.df)
  names(new.table ) <- region.for.table
  stat.tables.for.regions <- c(stat.tables.for.regions ,new.table)
}
@
<<SidewayTable_Creator_postcing,echo=FALSE,eval=TRUE>>=
# Separate hemispheres only for postcing
# Separate based on gender for all
# Ideally the separation based on gender  would be done 
# on a  measure(SA, vol,thickness) basis
#for (region.for.table in c("stg" ,"mtg","itg",,"antcing")){
region.for.table<- "postcing"
print.table.lh.df <- summ.stats.tables[[region.for.table]]$lh 
  print.table.rh.df <-summ.stats.tables[[region.for.table]]$rh
  all.df.lf.stg  <- filter(all.df.lf, region==region.for.table)
  for (hemi.var in c( "lh","rh")){
    aov.test.results <- data.frame(sex=character(0),aggstat=character(0),Diag=character(0),Covariates=character(0),p_values= numeric(0))

    for (agg.stat.name in agg.stats.names){
      covar.col.all.sex <-c()
      pval.col.all.sex <-c()
      for (sex.var in c( "Male","Female")){

        aov.fit<- lm(LCDM.measure~YrsEd*age*Diag,data=all.df.lf.stg,
                      subset=(hemi==hemi.var)&(sex==sex.var)&(aggstat==agg.stat.name))
        aov.result <- Anova(aov.fit,type=3)

        if (is.data.frame(aov.result)){
        p.vals <- aov.result$`Pr(>F)`
        } else {
          aov.result <- aov.result[[1]]
        p.vals <- aov.result$`Pr(>F)`
        }
        # remove the intercept term regardless of significance
        p.vals[1]<-1
        #the last p.value is always NA
        p.vals[length(p.vals)]<-1

        var.names <- rownames(aov.result)
        var.names <-  gsub(" ","",var.names)
        names(p.vals)<- var.names
        p.value.for.Diag <- p.vals["Diag"]

        p.vals["Diag"] <- 1

        num.sig.vars <- sum(p.vals<p.cutoff)

        if (num.sig.vars>0) {

          sig.var.names <- var.names[p.vals<p.cutoff]
          sig.var.pvals <- p.vals[p.vals<p.cutoff]
          sig.var.pvals <- formatC(sig.var.pvals, digits = 3,drop0trailing=TRUE)
          sig.covar.table.col <- paste(sig.var.names,"(p=", sig.var.pvals ,")")          
        }

        covar.col <- rep("",5)
        pval.col <- rep("",5)
        if (num.sig.vars==0) {
          covar.col[1]<- "None"
        } 
        else {
          covar.col[1:num.sig.vars] <- sig.covar.table.col
        }
        p.vals <- formatC(p.vals, digits = 3,drop0trailing=TRUE)
        pval.col[1]  <-  formatC(p.value.for.Diag, digits = 3,drop0trailing=TRUE)
        unit.block <- data.frame(sex=sex.var,aggstat=agg.stat.name, Diag= unique(all.df.lf.stg$Diag),Covariates=covar.col,p_values= pval.col)
        aov.test.results <- rbind(aov.test.results,unit.block)
        #covar.col.all.sex <- c(covar.col.all.sex,covar.col)
        #pval.col.all.sex  <- c(pval.col.all.sex,pval.col)
      }  
    }

    if (hemi.var=="lh") print.table.lh.df <- merge(print.table.lh.df, aov.test.results,  by = c("aggstat","Diag","sex"),sort=FALSE )
    if  (hemi.var=="rh") print.table.rh.df <- merge(print.table.rh.df, aov.test.results,  by = c("aggstat","Diag","sex"),sort=FALSE )

  }

  print.table.merged.df <-merge(print.table.rh.df,print.table.lh.df, by = c("aggstat","sex","Diag"),suffixes=c(".rh",".lh"),sort=FALSE)

  new.table <- list(print.table.merged.df)
  names(new.table ) <- region.for.table
  stat.tables.for.regions <- c(stat.tables.for.regions ,new.table)
#}
@

<<Table_3_pre, results='asis', eval=FALSE,echo=FALSE>>=
  #class(summary_table_1.df)<-"data.frame"
  table.out <- xtable(stat.tables.for.regions[["stg"]])
  print.xtable(table.out,floating.environment="sidewaystable" , include.rownames=FALSE,include.colnames=TRUE)
  @

\newpage
\begin{sidewaystable}
  \centering
	\footnotesize
	\begin{tabular}{l|rr|rr|rr|rr}
	\hline
	\textbf{Region} & & & \multicolumn{2}{c}{Right} \T & \multicolumn{2}{|c}{Left} & & \\
	\multicolumn{1}{l|}{Measure} \T\B & Gender & Diag & Mean & SD & Mean & SD & Covariate & P \\
	\hline\hline
	<<Table_3_stg, results='asis', eval=TRUE,echo=FALSE>>=
  #class(summary_table_1.df)<-"data.frame"
  #stat.tables.for.regions[["stg"]]$aggstat<-

  table.out <- xtable(stat.tables.for.regions[["stg"]])
  print.xtable(table.out, only.contents=TRUE, include.rownames=FALSE,include.colnames=FALSE,hline.after=5*(1:6))
  @

                \end{tabular}
	\caption{\textbf{STG  Measure}.  Statistics for each geometric feature of the STG.  ANCOVA results showing significant covariates. T=thickness, V=volume, and S=surface area.}
	\label{Wave1.STG.ANCOVA.b}
  \end{sidewaystable}

  \newpage
\begin{sidewaystable}
  \centering
  \footnotesize
	\begin{tabular}{l|rr|rr|rr|rr}
	\hline
	\textbf{Region} & & & \multicolumn{2}{c}{Right} \T & \multicolumn{2}{|c}{Left} & & \\
	\multicolumn{1}{l|}{Measure} \T\B & Gender & Diag & Mean & SD & Mean & SD & Covariate & P \\
	\hline\hline
	<<Table_3_mtg, results='asis', eval=TRUE,echo=FALSE>>=
  #class(summary_table_1.df)<-"data.frame"
  #stat.tables.for.regions[["stg"]]$aggstat<-

  table.out <- xtable(stat.tables.for.regions[["mtg"]])
  print.xtable(table.out, only.contents=TRUE, include.rownames=FALSE,include.colnames=FALSE,hline.after=5*(1:6))
  @

                \end{tabular}
	\caption{\textbf{MTG  Measure}.  Statistics for each geometric feature of the MTG.  ANCOVA results showing significant covariates. T=thickness, V=volume, and S=surface area.}
	\label{Wave1.MTG.ANCOVA.b}
  \end{sidewaystable}

  \newpage
\begin{sidewaystable}
  \centering
  \footnotesize
  \begin{tabular}{l|rr|rr|rr|rr}
	\hline
	\textbf{Region} & & & \multicolumn{2}{c}{Right} \T & \multicolumn{2}{|c}{Left} & & \\
	\multicolumn{1}{l|}{Measure} \T\B & Gender & Diag & Mean & SD & Mean & SD & Covariate & P \\
	\hline\hline
	<<Table_3_itg, results='asis', eval=TRUE,echo=FALSE>>=
  #class(summary_table_1.df)<-"data.frame"
  #stat.tables.for.regions[["stg"]]$aggstat<-

  table.out <- xtable(stat.tables.for.regions[["itg"]])
  print.xtable(table.out, only.contents=TRUE, include.rownames=FALSE,include.colnames=FALSE,hline.after=5*(1:6))
  @

                \end{tabular}
	\caption{\textbf{ITG  Measure}.  Statistics for each geometric feature of the ITG.  ANCOVA results showing significant covariates. T=thickness, V=volume, and S=surface area.}
	\label{Wave1.ITG.ANCOVA.b}
  \end{sidewaystable}

  \newpage
\begin{sidewaystable}
  \centering
  \footnotesize
  \begin{tabular}{l|rr|rrrr|rrrr|rr}
	\hline
	\textbf{Region} & & & \multicolumn{4}{c}{Right} \T & \multicolumn{4}{|c}{Left} & & \\
	\multicolumn{1}{l|}{Measure} \T\B & Gender & Diag & Mean & SD & Covariate & P & Mean & SD & Covariate & P \\
	\hline\hline
	<<Table_3_postcing, results='asis', eval=TRUE,echo=FALSE>>=

  table.out <- xtable(stat.tables.for.regions[["postcing"]])
  print.xtable(table.out, only.contents=TRUE, include.rownames=FALSE,include.colnames=FALSE,hline.after=5*(1:6))
  @

                \end{tabular}
	\caption{\textbf{Posterior Cingulate  Measure}.  Statistics for each geometric feature of the Posterior Cingulate.  ANCOVA results showing significant covariates. T=thickness, V=volume, and S=surface area.}
	\label{Wave1.postcing.ANCOVA.b}
  \end{sidewaystable}

  \newpage
\begin{sidewaystable}
  \centering
  \footnotesize
  \begin{tabular}{l|rr|rr|rr|rr}
  \hline
	\textbf{Region} & & & \multicolumn{2}{c}{Right} \T & \multicolumn{2}{|c}{Left} & & \\
	\multicolumn{1}{l|}{Measure} \T\B & Gender & Diag & Mean & SD & Mean & SD & Covariate & P \\
	\hline\hline
	<<Table_3_antcing, results='asis', eval=TRUE,echo=FALSE>>=
  #class(summary_table_1.df)<-"data.frame"
  #stat.tables.for.regions[["stg"]]$aggstat<-

  table.out <- xtable(stat.tables.for.regions[["antcing"]])
  print.xtable(table.out, only.contents=TRUE, include.rownames=FALSE,include.colnames=FALSE,hline.after=5*(1:6))
  @

                \end{tabular}
	\caption{\textbf{Anterior Cingulate  Measure}.  Statistics for each geometric feature of the Anterior Cingulate.  ANCOVA results showing significant covariates. T=thickness, V=volume, and S=surface area.}
	\label{Wave1.antcing.ANCOVA.b}
  \end{sidewaystable}

<<Pooled_Stat_Tests>>=
 side =  c("lh","rh")
  regions = c("itg","mtg","stg","antcing","postcing")
  conditions  = c("normal","aMCI","amdMCI","nMCI","nmdMCI")
  comparisons = t(array(1,2,1,3,1,4,1,5,2,3,2,4,4,5,dim = c(2,7)))

  cond_1_fileh <- open(file = paste0(DATA_DIR,"/",side,'_',region,"_",cond_1,"_wave1_pooled_antsy.txt"))
  cond_2_fileh <- open(file = paste0(DATA_DIR,"/",side,'_',region,"_",cond_2,"_wave1_pooled_antsy.txt"))

@

\newpage
\begin{sidewaystable}
	\centering
	\footnotesize
	\begin{tabular}{rr|rrr|rrr|rrr}
		\hline
		\multicolumn{2}{c|}{Region} \T\B & \multicolumn{3}{c|}{KS test} & \multicolumn{3}{c|}{MWU test} & \multicolumn{3}{c}{Welch's t-test} \\
		& & two-sided & less & greater & two-sided & greater & less & two-sided & greater & less \\ \hline
		& aMCI vs norm\T & $<$.0001 & .0832 & $<$.0001 & $<$.0001 & 1 & $<$.0001 & $<$.0001 & 1 & $<$.0001 \\
		rh stg & nMCI vs norm & $<$.0001 & $<$.0001 & $<$.0001 & $<$.0001 & 1 & $<$.0001 & $<$.0001 & 1 & $<$.0001 \\
		& aMCI vs nMCI\T & $<$.0001 & .5210 & $<$.0001 & $<$.0001 & 1 & $<$.0001 & $<$.0001 & 1 & $<$.0001 \\ \hline
		& aMCI vs norm & $<$.0001 & .9794 & $<$.0001 & $<$.0001 & 1 & $<$.0001 & $<$.0001 & 1 & $<$.0001 \\
		lh stg & nMCI vs norm & $<$.0001 & .9983 & $<$.0001 & $<$.0001 & 1 & $<$.0001 & $<$.0001 & 1 & $<$.0001 \\
		& aMCI vs nMCI & $<$.0001 & $<$.0001 & $<$.0001 & .0128 & .0064  & .9936 & $<$.0001 & $<$.0001 & 1 \\ \hline
		& aMCI vs norm\T & $<$.0001 & $<$.0001 & $<$.0001 & $<$.0001 & 1 & $<$.0001 & $<$.0001 & 1 & $<$.0001 \\
		rh stg & nMCI vs norm & $<$.0001 & .0121 & $<$.0001 & $<$.0001 & 1 & $<$.0001 & $<$.0001 & 1 & $<$.0001 \\
		(women)& aMCI vs nMCI & $<$.0001 & $<$.0001 & .0086 & .1065 & .0533 & .9467 & $<$.0001 & $<$.0001 & 1 \\ \hline
		& aMCI vs norm\T & $<$.0001 & .9989 & $<$.0001 & $<$.0001 & 1 & $<$.0001 & $<$.0001 & 1 & $<$.0001 \\
		lh stg & nMCI vs norm & $<$.0001 & .9998 & $<$.0001 & $<$.0001 & 1 & $<$.0001 & $<$.0001 & 1 & $<$.0001 \\
		(women)& aMCI vs nMCI & $<$.0001 & $<$.0001 & .0032 & .0060 & .0030 & .9970 & $<$.0001 & $<$.0001 & 1 \\ \hline
		& aMCI vs norm\T & $<$.0001 & .0396 & $<$.0001 & $<$.0001 & 1 & $<$.0001 & $<$.0001 & 1 & $<$.0001 \\
		rh mtg & nMCI vs norm & $<$.0001 & $<$.0001 & $<$.0001 & .5428 & .7286 & .2714 & $<$.0001 & 1 & $<$.0001 \\
		& aMCI vs nMCI & $<$.0001 & .4099 & $<$.0001 & $<$.0001 & 1 & $<$.0001 & $<$.0001 & 1 & $<$.0001 \\ \hline
		& aMCI vs norm\T & $<$.0001 & 1 & $<$.0001 & $<$.0001 & 1 & $<$.0001 & $<$.0001 & 1 & $<$.0001 \\
		lh mtg & nMCI vs norm & $<$.0001 & 1 & $<$.0001 & $<$.0001 & 1  & $<$.0001 & $<$.0001 & 1 & $<$.0001 \\
		& aMCI vs nMCI & $<$.0001 & .0296 & $<$.0001 & $<$.0001 & 1 & $<$.0001 & $<$.0001 & 1 & $<$.0001 \\ \hline
		& aMCI vs norm\T &  $<$.0001 & $<$.0001 & $<$.0001 & .5723 & NA & NA & .8289 & NA & NA \\
		rh itg & nMCI vs norm & $<$.0001 & $<$.0001 & .7620 & $<$.0001 & $<$.0001 & 1 & $<$.0001 & $<$.0001 & 1 \\
		& aMCI vs nMCI & $<$.0001 & .5502 & $<$.0001 & $<$.0001 & 1 & $<$.0001 & $<$.0001 & 1 & $<$.0001 \\ \hline
		& aMCI vs norm\T &  $<$.0001 & .8740 & $<$.0001 &  $<$.0001 & 1 & $<$.0001 &  $<$.0001 & 1 & $<$.0001 \\
		lh itg & nMCI vs norm & $<$.0001 & .7938 & $<$.0001 & $<$.0001 & 1 & $<$.0001 & $<$.0001 & 1 & $<$.0001 \\
		& aMCI vs nMCI & $<$.0001 & .8740 & $<$.0001 & $<$.0001 & 1 & $<$.0001 & $<$.0001 & 1 & $<$.0001 \\
	\end{tabular}
	\caption{\textbf{Temporal Lobe Pooled LCDM Analysis Results.}  Showing p-values obtained from nonparametric distribution tests.}
	\label{Wave1.TL.nonpara}
\end{sidewaystable}

\newpage
\begin{sidewaystable}
	\centering
	\footnotesize
	\begin{tabular}{rr|rrr|rrr|rrr}
		\hline
		\multicolumn{2}{c|}{Region} \T\B & \multicolumn{3}{c|}{KS test} & \multicolumn{3}{c|}{MWU test} & \multicolumn{3}{c}{Welch's t-test} \\
		& & two-sided & less & greater & two-sided & greater & less & two-sided & greater & less \\ \hline
		& aMCI vs norm\T &  $<$.0001 & $<$.0001 & .9896 &  $<$.0001 & $<$.0001 & 1 &  $<$.0001 & $<$.0001 & 1 \\
		rh antcing & nMCI vs norm & .0047 & .0024 & .9696 & .0496 & .0248 & .9752 & .0463 & .0232 & .9768 \\
		& aMCI vs nMCI & $<$.0001 & $<$.0001 & .9986 & $<$.0001 & $<$.0001 & .9986 & $<$.0001 & $<$.0001 & 1 \\ \hline
		& aMCI vs norm\T & $<$.0001 & $<$.0001 & .8789 & $<$.0001 & $<$.0001 & 1 & $<$.0001 & $<$.0001 & 1 \\
		lh antcing & nMCI vs norm & $<$.0001 & $<$.0001 & .6552 & $<$.0001 & $<$.0001 & 1 & $<$.0001 & $<$.0001 & 1 \\
		& aMCI vs nMCI & $<$.0001 & $<$.0001 & .9725 & $<$.0001 & $<$.0001 & 1 & $<$.0001 & $<$.0001 & 1 \\ \hline
		& aMCI vs norm\T & .0001 & $<$.0001 & .0043 & .2136 & .1068 & .8932 & .5986 & .2993 & .7007 \\
		rh postcing & nMCI vs norm & $<$.0001 & 1 & $<$.0001 & $<$.0001 & 1 & $<$.0001 & $<$.0001 & 1 & $<$.0001 \\
		& aMCI vs nMCI & $<$.0001 & $<$.0001 & .9786 & $<$.0001 & $<$.0001 & .9786 & $<$.0001 & $<$.0001 & 1 \\ \hline
		& aMCI vs norm\T & $<$.0001 & .9911 & $<$.0001 & $<$.0001 & 1 & $<$.0001  & $<$.0001 & 1 & $<$.0001  \\
		lh postcing & nMCI vs norm & $<$.0001 & .9971 & $<$.0001 & $<$.0001 & 1 & $<$.0001 & $<$.0001 & 1 & $<$.0001 \\
		& aMCI vs nMCI & $<$.0001 & $<$.0001 & .8553 & $<$.0001 & $<$.0001 & 1 & $<$.0001 & $<$.0001 & 1 \\
	\end{tabular}
	\caption{\textbf{Cingulate Gryus Pooled LCDM Analysis Results}   Showing p-values obtained from nonparametric distribution tests.}
	\label{Wave1.cing.nonpara}
\end{sidewaystable}

\end{document}

### 2016-02-29 src/LCDM_wave1_wave2_pooled.r

@@ -22,7 +22,7 @@ dists=sapply(distsl,sample,minlength) #for tests requiring same number in group
 
 ######### Simple Summary Statistics ########
 
-pdf(file=paste("wave1_wave2/summarystat_",REGION,"_",DIAG,".pdf",sep=''))
+pdf(file=paste("wave1_wave2/summarystat_",REGION,"_",DIAGs,".pdf",sep=''))
 
 col=c('black','red')
 thk95<-c()
@@ -66,8 +66,8 @@ b[[3]]<-ks.test(distsl[[2]],distsl[[1]],alternative="g",exact=NULL)
 return(b)
 }
 
-file1=paste("/cis/project/sydney/pooled_analysis/pooled_files_wave1wave2/",REGION,"_",DIAG,"_wave1_pooled_antsy.txt",sep="")
-file2=paste("/cis/project/sydney/pooled_analysis/pooled_files_wave1wave2/",REGION,"_",DIAG,"_wave2_pooled_antsy.txt",sep="")
+file1=paste("./pooled_files_wave1wave2/",REGION,"_",DIAGs[1],"_wave1_pooled_antsy.txt",sep="")
+file2=paste("./pooled_files_wave1wave2/",REGION,"_",DIAGs[2],"_wave1_pooled_antsy.txt",sep="")
 
 fileNames=c(file1,file2)
 
@@ -84,7 +84,7 @@ out<-LCDM(fileNames,condTests,REGION)
 
 ### write results into file ###
 
-OUTFILE=paste("/cis/project/sydney/pooled_analysis/wave1_wave2/result_",REGION,"_",DIAG,".txt",sep='')
+OUTFILE=paste("./results/Pooled_test_results_",REGION,"_",DIAGs,".txt",sep='')
 
 #cat("Statistical Summary for ",REGION,"\n",file=OUTFILE)
 

### 2016-02-29 src/pool_LCDM_stats.py

@@ -29,7 +29,9 @@ diags=[
 #    normtest2_aMCI
 ]
 
-hemis=['rh','lh']
+
+hemis = ['rh','lh']
+
 
 wave1_dir1 = '/cis/project/sydney/data_fslcdm/MAS.20100921_Antsy/'
 wave1_dir2 = '/cis/project/sydney/data_fslcdm/MAS.20110324_Antsy/'
@@ -41,41 +43,42 @@ for region in regions:
             idfile=join_p(ROOT,'data','ids_5_subclass','Diag_'+diag+'_ID_list.csv' ) #wave1_${diag}_used.txt'
             id_fh = open(idfile,'r')
             ids = id_fh.readlines()
-            for id in ids:
 
-                for sub in subregions[region]:
-                    sub_region=hemi+'_'+sub
-                    output_dir = join_p(ROOT,'data','pooled_analysis','pooled_5subclass_antsy_files_used')
-                    if not os.path.exists(output_dir):
-                        os.makedirs(output_dir)
-                    output_fname = join_p(output_dir,sub_region+'_'+diag+'_wave1_pooled_antsy.txt')
-                    #of_handle = open (output_fname,'a')
 
-                    for id in ids:
-                        id = id.strip()
-                        full_dir_names = os.listdir(wave1_dir1)
-                    #   full_path =  os.path.join(wave1_dir1, x for x in full_dir_names if x.startswith(id), 'FSLCDM_v2.3',region_name,sub_region+'_1_manseg_quartile_pialmsk_AntsyGrey.txt')
-                        full_path =  os.path.join(wave1_dir1, id+"*", 'FSLCDM_v2.3',region_name,sub_region+'_1_manseg_quartile_pialmsk_AntsyGrey.txt')
-                        print full_path
+            for sub in subregions[region]:
+                sub_region=hemi+'_'+sub
+                output_dir = join_p(ROOT,'data','pooled_analysis','pooled_5subclass_antsy_files_used')
+                if not os.path.exists(output_dir):
+                    os.makedirs(output_dir)
+                output_fname = join_p(output_dir,sub_region+'_'+diag+'_wave1_pooled_antsy.txt')
+                #of_handle = open (output_fname,'a')
+
+                for id in ids:
+                    id = id.strip()
+                    full_dir_names = os.listdir(wave1_dir1)
[…]

### 2016-02-29 src/ArticleReadyTableGenerate.Rnw
add pooled stat testing. not working yet

@@
 <<Pooled_Stat_Tests>>=
+  DATA_DIR = "./data/pooled_analysis/"
  side =  c("lh","rh")
@@
   comparisons = t(array(1,2,1,3,1,4,1,5,2,3,2,4,4,5,dim = c(2,7)))
+  pooled_stats_list = list()
 
-  cond_1_fileh <- open(file = paste0(DATA_DIR,"/",side,'_',region,"_",cond_1,"_wave1_pooled_antsy.txt"))
-  cond_2_fileh <- open(file = paste0(DATA_DIR,"/",side,'_',region,"_",cond_2,"_wave1_pooled_antsy.txt"))
+  #read the pooled files 
+  for (i in 1:5) {
+    cond_fileh <- open(file = paste0(DATA_DIR,"/",side,'_',region,"_", conditions[i], "_wave1_pooled_antsy.txt"))
+    pooled_stats_list <-read.table(cond_fileh, nrows = 2.5E6, colClasses = "numeric")
+    if ( is.data.frame(pooled_stats_list) ) {
+      pooled_stats_list <- pooled_stats_list[,1]
+    }
+    pooled_stats_list <-c(pooled_stats_list, list(pool_stats)) 
+  }
+  # run the stat tests for the 7 pair comparisons. We may want to limi
+  for ( i in 1:7 ) {
+    cond_1 = comparisons[i,1]
+    cond_2 = comparisons[i,2]
+     pooled_test_result[[i]] <- wilcox.test(pooled_stats_list[[cond_2]], pooled_stats_list[[cond_1]],
+                               alternative="t",exact = FALSE,
+                               correct = FALSE)
+      pooled_test_result[[i]] <- ks.test(pooled_stats_list[[cond_2]], pooled_stats_list[[cond_1]],
+                           alternative="t",exact = NULL)
+
+    pooled_test_result[[i]] <- ks.test(pooled_stats_list[[cond_2]], pooled_stats_list[[cond_1]],    
+                                       alternative = "t",mu = 0, paired = FALSE, 
+                           var.equal = FALSE, conf.level = 0.95)
+
+  }
 

### 2016-08-12 src/ArticleReadyTableGenerate.Rnw
added  pooled stat tests

--- 2016-02-29 src/ArticleReadyTableGenerate.Rnw
@@
 
-<<LoadData_and_BasicDataMunge,echo=FALSE,results='hide',warning=FALSE, message=FALSE>>=
+<<LoadData_and_BasicDataMunge,echo=FALSE,results='hide',warning=FALSE, message=FALSE,cache=FALSE>>=
 # Load Data
@@
 print(HOME_DIR)
-setwd(HOME_DIR)
-setwd("./projects/MAS_Score_Analysis")
+opts_knit$set(root.dir=paste0(Sys.getenv("HOME"),"/projects/MAS_Score_Analysis/",sep="",collapse=""))
+#setwd("./projects/MAS_Score_Analysis")
 #setwd( paste0(Sys.getenv("HOME"),"/projects/MAS_Score_Analysis/"))
 #The script gets data from  SPSS files, merges data frames to one data frame
-source("./src/MAS_MCIsubtype_analysis.R")
+source( paste0(Sys.getenv("HOME"),"/projects/MAS_Score_Analysis/","./src/MAS_MCIsubtype_analysis.R",sep="",collapse=""))
 all.df<- droplevels(all.df)
@@
 		& \B & & Mean & SD & Mean & SD \\ \hline
-<<Table_1_summarystats, results='asis', eval=TRUE,echo=FALSE>>=
+<<Table_1_summarystats, results='asis', eval=TRUE,echo=FALSE,cache=FALSE>>=
   class(summary_table_1.df)<-"data.frame"
@@
 <<Pooled_Stat_Tests>>=
- side =  c("lh","rh")
+  DATA_DIR = "./data/pooled_analysis/"
+  sides =  c("lh","rh")
   regions = c("itg","mtg","stg","antcing","postcing")
   conditions  = c("normal","aMCI","amdMCI","nMCI","nmdMCI")
-  comparisons = t(array(1,2,1,3,1,4,1,5,2,3,2,4,4,5,dim = c(2,7)))
+  comparisons = t(array(c(1,2,1,3,1,4,1,5,2,3,2,4,4,5),dim = c(2,7)))
 
-  cond_1_fileh <- open(file = paste0(DATA_DIR,"/",side,'_',region,"_",cond_1,"_wave1_pooled_antsy.txt"))
-  cond_2_fileh <- open(file = paste0(DATA_DIR,"/",side,'_',region,"_",cond_2,"_wave1_pooled_antsy.txt"))
+  pool_stat_tests_all_regions_sides<- list(lh = NULL, rh = NULL)
+  for ( side in sides) {
+    pool_stat_tests_all_regions_sides[[side]] = list()
+    for ( region in regions ) {
+      pooled_stats_list = list()
+
+      #read the pooled files 
+      for (i in 1:5) {
+        cond_fileh <- paste(DATA_DIR,"/",side,'_',region,"_", conditions[i], 
+                            "_wave1_pooled_antsy.txt", sep="", collapse ="")
+        print (cond_fileh)
+        if (! file.exists(cond_fileh)) {
+          print (paste0( cond_fileh,
+                         " does not exist",sep="",collapse="") )
+        }
+        pooled_stats <-read.table(file=cond_fileh, nrows = 2.5E6, colClasses = "numeric")
+        print (str(pooled_stats_list))
+        if ( is.data.frame(pooled_stats_list) ) {
+          pooled_stats <- pooled_stats[,1]
+        }
+        pooled_stats_list <-c(pooled_stats_list,list(pooled_stats))
+
+      }
+      pool_stat_tests_all_regions_sides[[side]] <-c(pool_stat_tests_all_regions_sides[[side]], list(pooled_stats_list)) 
+      #run the stat tests for the 7 pair comparisons. We may want to limi
+      pooled_test_result<-list()
+      for ( i in 1:7 ) {
+        pooled_test_result <- c(pooled_test_result,list=list())
+      }
+
+      p_values<-list(mwu.test=rep(0,7), ks.test = rep(0,7), kolmog.test = rep(0,7))
+      for ( i in 1:7 ) {
+        cond_1 = comparisons[i,1]
+        cond_2 = comparisons[i,2]
+
+        pooled_test_result[[i]] <- ks.test(pooled_stats_list[[cond_2]], pooled_stats_list[[cond_1]],
+                                           alternative="t",exact = NULL)
+        p_values$ks.test[i] <-pooled_test_result[[i]]$p.value
+
+        pooled_test_result[[i]] <- wilcox.test(pooled_stats_list[[cond_2]], pooled_stats_list[[cond_1]],
+                                               alternative="t",exact = FALSE,
+                                               correct = FALSE)
+        p_values$mwu.test[i] <-pooled_test_result[[i]]$p.value
+        pooled_test_result[[i]] <- t.test(pooled_stats_list[[cond_2]], pooled_stats_list[[cond_1]],    
+                                           alternative = "t",mu = 0, paired = FALSE, 
+                                           var.equal = FALSE, conf.level = 0.95)
+
+        p_values$welcht.test[i] <-pooled_test_result[[i]]$p.value
+      }
+      pool_stat_tests_all_regions_sides[[side]] <- c(pool_stat_tests_all_regions_sides[[side]],list(pooled_test_result) )
+    }
+    names(pool_stat_tests_all_regions_sides[[side]]) <- regions
+  }
 

### 2016-08-12 src/MAS_MCIsubtype_analysis.R
set home directory in subscript

@@ -1,5 +1,8 @@
 library(foreign)
 #Read cognitive score and Dx files
+HOME_DIR <- Sys.getenv("HOME")
+
+setwd(paste0(HOME_DIR,"/projects/MAS_Score_Analysis/",collapse=""))
 MAS.normal.df <- read.spss("./data/M_w123_npsych_v20130718/M_all_npsych_normal_v20120921.sav")
 
 MAS.normal.df<- as.data.frame(MAS.normal.df[c(1:17,143:180,184:203,207:209)])

### 2016-08-14 src/ArticleReadyTableGenerate.Rnw
getting ready to run pooled LCDM tests, once directory structures are correct

@@
 
-<<Pooled_Stat_Tests>>=
+<<Pooled_Stat_Tests,cache=TRUE>>=
   DATA_DIR = "./data/pooled_analysis/"
@@
   comparisons = t(array(c(1,2,1,3,1,4,1,5,2,3,2,4,4,5),dim = c(2,7)))
+  hypothesis_ordinality <- c("two.sided","less","greater")
 
-  pool_stat_tests_all_regions_sides<- list(lh = NULL, rh = NULL)
+  pool_stat_tests_all_regions_sides <- matrix(list(), nrow=2,ncol=5,dimnames = list(sides=sides,regions=regions))
+
+  print (str(pool_stat_tests_all_regions_sides))
+  pool_stats_all <-  matrix(rep(c(),10), nrow=2,ncol=5,dimnames = list(sides=sides,regions=regions))
   for ( side in sides) {
-    pool_stat_tests_all_regions_sides[[side]] = list()
+
     for ( region in regions ) {
+
       pooled_stats_list = list()
@@
         }
-        pooled_stats <-read.table(file=cond_fileh, nrows = 2.5E6, colClasses = "numeric")
+        #pooled_stats <-read.table(file=cond_fileh, nrows = 2.5E6, colClasses = "numeric")
+        pooled_stats <- scan(file=cond_fileh)
         print (str(pooled_stats_list))
         if ( is.data.frame(pooled_stats_list) ) {
-          pooled_stats <- pooled_stats[,1]
+          pooled_stats <- as.vector(pooled_stats[,1])
         }
         pooled_stats_list <-c(pooled_stats_list,list(pooled_stats))
+      }
+      print(str(pool_stats_all[side,region]))
+      print(str(pooled_stats_list))
+      #pool_stats_all[side,region] <- c(pool_stats_all[side,region],pooled_stats_list)
+      pool_stats_all[side,region] <- pooled_stats_list
 
+      #run the stat tests for the 7 pair comparisons. We may want to limi
+      pooled_test_results<-list()
+      for ( i in 1:7 ) {
+        pooled_test_results <- c(pooled_test_results,list=list())
       }
-      pool_stat_tests_all_regions_sides[[side]] <-c(pool_stat_tests_all_regions_sides[[side]], list(pooled_stats_list)) 
-      #run the stat tests for the 7 pair comparisons. We may want to limi
-      pooled_test_result<-list()
-      for ( i in 1:7 ) {
-        pooled_test_result <- c(pooled_test_result,list=list())
-      }
+      empty.df <- data.frame( two.sided=rep(0,7),less= rep(0,7),greater=rep(0,7) )
+      p_values<-list(mwu.test=empty.df, ks.test = empty.df, welch.t.test=empty.df)
 
-      p_values<-list(mwu.test=rep(0,7), ks.test = rep(0,7), kolmog.test = rep(0,7))
       for ( i in 1:7 ) {
@@
         cond_2 = comparisons[i,2]
+        pooled_test_results[[i]] <-list(two.sided=c(),less=c(),greater=c())
+        for (test.type in  hypothesis_ordinality) {
 
-        pooled_test_result[[i]] <- ks.test(pooled_stats_list[[cond_2]], pooled_stats_list[[cond_1]],
-                                           alternative="t",exact = NULL)
-        p_values$ks.test[i] <-pooled_test_result[[i]]$p.value
+        kolmog.test.result<- ks.test(pooled_stats_list[[cond_2]], pooled_stats_list[[cond_1]],
+                                           alternative=test.type,exact = NULL)
+        p_values$ks.test[i,][test.type] <-kolmog.test.result$p.value
 
-        pooled_test_result[[i]] <- wilcox.test(pooled_stats_list[[cond_2]], pooled_stats_list[[cond_1]],
-                                               alternative="t",exact = FALSE,
+        wilcox.test.result <- wilcox.test(pooled_stats_list[[cond_2]], pooled_stats_list[[cond_1]],
+                                               alternative=test.type,exact = FALSE,
                                                correct = FALSE)
-        p_values$mwu.test[i] <-pooled_test_result[[i]]$p.value
-        pooled_test_result[[i]] <- t.test(pooled_stats_list[[cond_2]], pooled_stats_list[[cond_1]],    
-                                           alternative = "t",mu = 0, paired = FALSE, 
+        p_values$mwu.test[i,][test.type] <-wilcox.test.result$p.value
+        welch.t.test.result <- t.test(pooled_stats_list[[cond_2]], pooled_stats_list[[cond_1]],    
+                                           alternative = test.type,mu = 0, paired = FALSE, 
                                            var.equal = FALSE, conf.level = 0.95)
 
-        p_values$welcht.test[i] <-pooled_test_result[[i]]$p.value
+        p_values$welch.t.test[i,][test.type] <-welch.t.test.result$p.value
+       pooled_test_results[[i]][test.type] <-list(ks.test=kolmog.test.result,wilcox.test = wilcox.test.result,t.test= welch.t.test.result)
       }
-      pool_stat_tests_all_regions_sides[[side]] <- c(pool_stat_tests_all_regions_sides[[side]],list(pooled_test_result) )
+
     }
-    names(pool_stat_tests_all_regions_sides[[side]]) <- regions
+    pool_stat_tests_all_regions_sides[side,region] <- c(pool_stat_tests_all_regions_sides[side,region],pooled_test_results)
+  }
 }

### 2016-09-30 src/MAS_MCIsubtype_analysis.R
commits from detached head

@@ -8,9 +8,9 @@ MAS.normal.df<- as.data.frame(MAS.normal.df[c(1:17,143:180,184:203,207:209)])
 MAS.healthy.df <- read.spss("./data/M_w123_npsych_v20130718/M_all_npsych_healthy_v20120921.sav")
 MAS.healthy.df<- as.data.frame(MAS.healthy.df[c(1:14,140:177,181:200,204:206)])
 
-
+# We use the subclassification from  M_123_dx_v20121023.sav
 MCI_class <- read.spss("./data/M_123_dx_v20121023.sav")
-subclass.df<-as.data.frame(MCI_class[c(1:3,11,27,44)])
+subclass.df<-as.data.frame(MCI_class[c(1:3,7,8,11,27,44)])
 #W1_subclass <- read.csv("./data/W1_MCI classifications_NORMS_based_ESBs only_for Anne.csv")
 #W2_subclass <- read.csv("./data/MAS W1and2_Diagnostic_classifications.csv")
 
@@ -22,6 +22,9 @@ W1_dir_tag_s <- "_MAS.20110324"
 W2_dir_tag <- "_wave2"
 subregions <- outer(c("lh_","rh_"),c("stg","itg","mtg","antcing","postcing"),paste0)
 
+
+# Read (prev. computed)aggregate statistics of LCDM measure from csv files
+# put them in data frames where columns are subregions
 #wave 1 files
 OUTPUT_DIR <- "./data/"
 DATA_DIR <- ""
@@ -167,15 +170,15 @@ MAS.healthy.df$ID<-substr(as.character(MAS.normal.df$ID),1,4)
 all.files.merged.df <-merge(MAS.normal.df,MAS.healthy.df, by="ID")
 all.files.merged.df <- merge(all.files.merged.df,LCDM_thick_W1, by="ID",all.x=TRUE)
 all.files.merged.df <- merge(all.files.merged.df,LCDM_vol_W1, by="ID",all.x=TRUE,
-                             suffixes=c("thick_W1","vol_W1"))
+                             suffixes=c("_thick_W1","_vol_W1"))
 all.files.merged.df <- merge(all.files.merged.df,LCDM_surfarea_W1, by="ID",all.x=TRUE,
-                             suffixes=c("vol_W1","surfarea_W1"))
+                             suffixes=c("_vol_W1","_surfarea_W1"))
 all.files.merged.df <- merge(all.files.merged.df,LCDM_thick_W2, by="ID",all.x=TRUE,
[…]

### 2016-10-02 src/ArticleReadyTableGenerate.Rnw
fix pooled tests

@@
 
-<<Pooled_Stat_Tests,cache=TRUE>>=
+<<Pooled_Stat_Tests, cache=TRUE>>=
   DATA_DIR = "./data/pooled_analysis/"
@@
   print (str(pool_stat_tests_all_regions_sides))
-  pool_stats_all <-  matrix(rep(c(),10), nrow=2,ncol=5,dimnames = list(sides=sides,regions=regions))
+  #pool_stats_all <-  matrix(nrow=2,ncol=5,dimnames = list(sides=sides,regions=regions))
+  #pool_stats_all <- list(NULL, names=)
   for ( side in sides) {
@@
       }
-      print(str(pool_stats_all[side,region]))
+      #print(str(pool_stats_all[side,region]))
       print(str(pooled_stats_list))
       #pool_stats_all[side,region] <- c(pool_stats_all[side,region],pooled_stats_list)
-      pool_stats_all[side,region] <- pooled_stats_list
+      #pool_stats_all[side,region] <- pooled_stats_list
 
@@
         cond_2 = comparisons[i,2]
-        pooled_test_results[[i]] <-list(two.sided=c(),less=c(),greater=c())
+        pooled_test_results[[i]] <-list(two.sided=list(),less=list(),greater=list())
         for (test.type in  hypothesis_ordinality) {
@@
         p_values$welch.t.test[i,][test.type] <-welch.t.test.result$p.value
-       pooled_test_results[[i]][test.type] <-list(ks.test=kolmog.test.result,wilcox.test = wilcox.test.result,t.test= welch.t.test.result)
+       pooled_test_results[[i]][[test.type]]<-vector(mode="list",length = 3 )
+       print(str(pooled_test_results[[i]][[test.type]]))
+       pooled_test_results[[i]][[test.type]]<-list(ks.test=kolmog.test.result,wilcox.test = wilcox.test.result,t.test= welch.t.test.result)
+       print(str(pooled_test_results[[i]][[test.type]]))
       }
@@
     }
-    pool_stat_tests_all_regions_sides[side,region] <- c(pool_stat_tests_all_regions_sides[side,region],pooled_test_results)
+    pool_stat_tests_all_regions_sides[side,region] <- list(pooled_test_results)
   }

### 2016-10-02 src/ArticleReadyTableGenerate.Rnw
turn off warnings

@@
 
-<<Pooled_Stat_Tests, cache=TRUE>>=
+<<Pooled_Stat_Tests, cache=TRUE,echo=FALSE>>=
   DATA_DIR = "./data/pooled_analysis/"
@@
       #print(str(pool_stats_all[side,region]))
-      print(str(pooled_stats_list))
+      #print(str(pooled_stats_list))
       #pool_stats_all[side,region] <- c(pool_stats_all[side,region],pooled_stats_list)
@@
        pooled_test_results[[i]][[test.type]]<-vector(mode="list",length = 3 )
-       print(str(pooled_test_results[[i]][[test.type]]))
+       #print(str(pooled_test_results[[i]][[test.type]]))
        pooled_test_results[[i]][[test.type]]<-list(ks.test=kolmog.test.result,wilcox.test = wilcox.test.result,t.test= welch.t.test.result)
-       print(str(pooled_test_results[[i]][[test.type]]))
+       #print(str(pooled_test_results[[i]][[test.type]]))
       }

### 2016-10-09 src/ArticleReadyTableGenerate.Rnw
added table generation for pooled LCDM

@@
 
-<<Pooled_Stat_Tests, cache=TRUE,echo=FALSE>>=
+<<Pooled_Stat_Tests, cache=TRUE,echo=FALSE,warning=FALSE>>=
   DATA_DIR = "./data/pooled_analysis/"
@@
 
+<<echo=FALSE, results='asis' >>=
+
+  cond_1 = conditions[comparisons[,1]]
+  cond_2 = conditions[comparisons[,2]]
+  comparison_strings <- paste(cond_1,cond_2, sep =" vs ")
+  test_names <- c("KS test","MWU test", "Welch's t-test")
+  col_names <- outer(hypothesis_ordinality,test_names,paste,  sep=".")
+  p_value_table_names <-expand.grid(comparison_strings, col_names)
+  p_value_table <- matrix(0,nrow = 7,ncol = 9)
+
+  for (side in sides){
+    for ( i in 1:7 ) {
+      for (j in 1:3){
+        test.type <-  hypothesis_ordinality[j]
+        for (k in 0:2){
+          test.name <- names(pooled_test_results[[i]][[test.type]][(k+1)])
+        p_value_table[i,j + (k*3)] <- pooled_test_results[[i]][[test.type]][[test.name]]$p.value
+
+        }
+      }
+
+    }
+  }
+  colnames(p_value_table)<- col_names
+  xtab.out <- xtable(p_value_table)
+  addtorow <- list()
+  addtorow$pos <- list(0)
+  addtorow$command <- paste0(paste0('& \\multicolumn{3}{c}{', c("KS test","MWU test", "Welch's t-test"), '}', collapse=''), '\\\\')
+  print.xtable (xtab.out, add.to.row = addtorow, only.contents=TRUE,
+    include.rownames=FALSE,
+    type="latex")
+# create a table of 7 comparisons
+#
+
+@
+
 \newpage

### 2016-10-10 src/ArticleReadyTableGenerate.Rnw
Modify printed table

@@
   colnames(p_value_table)<- col_names
-  xtab.out <- xtable(p_value_table)
+  p_value_table_print <- mapply(p_value_table, function(x){if (x<1E-4) return ("<0.0001") else{
+    return(as.character(x,digits=4))
+  }})
+  xtab.out <- xtable(p_value_table_print)
   addtorow <- list()

### 2016-10-10 src/ArticleReadyTableGenerate.Rnw
Table is nearly generated independently. Need to correct column names and row names in table.

--- 2016-10-09 src/ArticleReadyTableGenerate.Rnw
@@
 <<echo=FALSE, results='asis' >>=
-
+ convert_to_paper_style <- function(x) {
+   if (x<1E-4) {
+   return ("<0.0001") 
+   } else {
+    return (as.character(x,digits=4))
+   }
+ }
+  make_matrix_printable <- Vectorize(convert_to_paper_style)
   cond_1 = conditions[comparisons[,1]]
@@
   colnames(p_value_table)<- col_names
-  xtab.out <- xtable(p_value_table)
+  table_dims<- dim(p_value_table)
+  p_value_table_print <- make_matrix_printable(p_value_table )
+  dim(p_value_table_print) <- table_dims
+  print(str(p_value_table_print))
+
+  xtab.out <- xtable(p_value_table_print)
   addtorow <- list()

### 2016-10-10 src/ArticleReadyTableGenerate.Rnw
working table needs column names

--- 2016-10-09 src/ArticleReadyTableGenerate.Rnw
@@
 <<echo=FALSE, results='asis' >>=
-
+ convert_to_paper_style <- function(x) {
+   if (x<1E-4) {
+   return ("<0.0001") 
+   } else {
+    return (format(x,digits=4))
+   }
+ }
+  make_matrix_printable <- Vectorize(convert_to_paper_style)
   cond_1 = conditions[comparisons[,1]]
@@
   colnames(p_value_table)<- col_names
-  xtab.out <- xtable(p_value_table)
+  table_dims<- dim(p_value_table)
+  p_value_table_print <- make_matrix_printable(p_value_table )
+  dim(p_value_table_print) <- table_dims
+  colnames(p_value_table_print) <- col_names
+  rownames(p_value_table_print) <- comparison_strings
+  print(str(p_value_table_print))
+
+  xtab.out <- xtable(as.data.frame(p_value_table_print  ) )
   addtorow <- list()
-  addtorow$pos <- list(0)
+  addtorow$pos <- list(-1)
   addtorow$command <- paste0(paste0('& \\multicolumn{3}{c}{', c("KS test","MWU test", "Welch's t-test"), '}', collapse=''), '\\\\')
   print.xtable (xtab.out, add.to.row = addtorow, only.contents=TRUE,
-    include.rownames=FALSE,
+    include.rownames=TRUE, include.colnames = TRUE,
     type="latex")

### 2016-10-11 src/ArticleReadyTableGenerate.Rnw
table is  now visible. is formatted properly. needs to be repeated for all sides and regions

--- 2016-10-10 src/ArticleReadyTableGenerate.Rnw
@@
 
+\begin{table}[t]
+  \centering
+	\begin{tabular}{rrrrrrr}
+		\hline
+
+	\end{tabular}
+	\caption{\textbf{Summary of data used for MCI analysis}.
+Summary statistics on the number, age, and years of education of individuals used for the analysis.
+Data broken down based on gender and diagnosis.}
+	\label{wave1data}
+\end{table}
+
 <<echo=FALSE, results='asis' >>=
-
+ convert_to_paper_style <- function(x) {
+   if (x<1E-4) {
+   return ("<0.0001") 
+   } else {
+    return (format(x,digits=4))
+   }
+ }
+  simp.colnames<- function(x) {
+     y = lapply(x,strsplit,"_",fixed=TRUE)
+     #return(y)
+     z = sapply(y , function(l) l[[1]][[1]])
+     #z = gsub(".", " ",y)
+    return (z)
+  }
+  make_matrix_printable <- Vectorize(convert_to_paper_style)
   cond_1 = conditions[comparisons[,1]]
@@
   test_names <- c("KS test","MWU test", "Welch's t-test")
-  col_names <- outer(hypothesis_ordinality,test_names,paste,  sep=".")
+  col_names <- outer(hypothesis_ordinality,test_names,paste,  sep="_")
   p_value_table_names <-expand.grid(comparison_strings, col_names)
   p_value_table <- matrix(0,nrow = 7,ncol = 9)
-
+  p_val_table_list<-list()
+  xtablelist<- list()
   for (side in sides){
@@
     }
+    colnames(p_value_table)<- col_names
+  table_dims<- dim(p_value_table)
+  p_value_table_print <- make_matrix_printable(p_value_table )
+  dim(p_value_table_print) <- table_dims
+  colnames(p_value_table_print) <- col_names
+  rownames(p_value_table_print) <- comparison_strings
+  #print(str(p_value_table_print))
+
+  xtab.out <- xtable( as.data.frame(p_value_table_print  ) )
+  p_val_table_list[[side]]<- p_value_table_print
+  xtablelist[[side]]<-xtab.out
+
   }
-  colnames(p_value_table)<- col_names
-  p_value_table_print <- mapply(p_value_table, function(x){if (x<1E-4) return ("<0.0001") else{
-    return(as.character(x,digits=4))
-  }})
-  xtab.out <- xtable(p_value_table_print)
+   attr(p_val_table_list, "subheadings") <- paste0("Hemisphere : ",names(p_val_table_list))
+   xtablelist <- xtableList(p_val_table_list)
   addtorow <- list()
-  addtorow$pos <- list(0)
+  addtorow$pos <- list(-1)
   addtorow$command <- paste0(paste0('& \\multicolumn{3}{c}{', c("KS test","MWU test", "Welch's t-test"), '}', collapse=''), '\\\\')
-  print.xtable (xtab.out, add.to.row = addtorow, only.contents=TRUE,
-    include.rownames=FALSE,
+  print.xtableList (xtablelist, add.to.row = addtorow, only.contents=FALSE,
+    include.rownames=TRUE, sanitize.colnames.function = simp.colnames,
     type="latex")
 # create a table of 7 comparisons
-#
 

### 2016-11-01 src/ArticleReadyTableGenerate.Rnw
finished pooled LCDM removed extra printouts

@@
 HOME_DIR <- Sys.getenv("HOME")
-print(HOME_DIR)
+#print(HOME_DIR)
 opts_knit$set(root.dir=paste0(Sys.getenv("HOME"),"/projects/MAS_Score_Analysis/",sep="",collapse=""))
@@
 
-<<ICVStats,eval=TRUE,error=TRUE,echo=FALSE>>=
+<<ICVStats,eval=TRUE,error=TRUE,echo=FALSE,results="hide">>=
 require(car)
@@
 # Does ICV show a trend level  group difference (Is p-value for Diag sig?)
-print("ICVStats ANOVA with covars")
-print(aov.result.type3)
+#print("ICVStats ANOVA with covars")
+#print(aov.result.type3)
 
 # Does ICV show a trend level  group difference (Is p-value for Diag sig?)
-print("ICVStats ANOVA")
-print(aov.result)
+#print("ICVStats ANOVA")
+#print(aov.result)
 
@@
 
-<<ICVStats_plot,  eval=TRUE,echo=FALSE>>=
+<<ICVStats_plot,  eval=TRUE,echo=FALSE,results="asis">>=
 summary_table_2.df  <- summarize (grouping_gender_diag, mean_ICV=mean(ICV_W1,na.rm=T), sd_ICV=sd(ICV_W1,na.rm=T))
@@
 }
-print(table.out, include.rownames=FALSE,include.colnames=TRUE)
 
 p_vals <- formatC(aov.result.summary$`Pr(>F)` [1:3], digits = 3,drop0trailing=TRUE)
-print (aov.result.summary)
+#print (aov.result.summary)
 Covariate_names <- rownames(aov.result.summary)[1:3]
-print(str(aov.result.summary))
-print(Covariate_names)
+#print(str(aov.result.summary))
+#print(Covariate_names)
 cov_column <- paste(Covariate_names,"(p = ",p_vals,")",sep="")
@@
 
+print(table.out, include.rownames=FALSE,include.colnames=TRUE)
 @
@@
 <<subregion_sideway_table_summary_stats,eval=TRUE,echo=FALSE>>=
+#print("subregion_sideway_table_summary_stats")
 stat.tables.for.regions <- list()
@@
 
+  all.df.lf.stg.lh$aggstat<- as.factor(all.df.lf.stg.lh$aggstat)
   all.df.lf.stg.lh.grp<- group_by(all.df.lf.stg.lh, aggstat, sex,Diag)
@@
 }
-print(str(summ.stats.tables))
+#print(str(summ.stats.tables))
 @
@@
              measure.name ))
+    print(names(all.df.lf))
     all.df.lf.stg    <- filter(all.df.lf, region==region.for.table & aggstat==measure.name)
@@
     }
-    print(covar.col.all.sex )
-    print(pval.col.all.sex )
+    #print(covar.col.all.sex )
+    #print(pval.col.all.sex )
     print.table.df <- merge(print.table.rh.df,print.table.lh.df,
@@
 
-  print (str(pool_stat_tests_all_regions_sides))
+  #print (str(pool_stat_tests_all_regions_sides))
   #pool_stats_all <-  matrix(nrow=2,ncol=5,dimnames = list(sides=sides,regions=regions))
@@
                             "_wave1_pooled_antsy.txt", sep="", collapse ="")
-        print (cond_fileh)
+        #print (cond_fileh)
         if (! file.exists(cond_fileh)) {
@@
         pooled_stats <- scan(file=cond_fileh)
-        print (str(pooled_stats_list))
+        #print (str(pooled_stats_list))
         if ( is.data.frame(pooled_stats_list) ) {
@@
 
-\begin{table}[t]
-  \centering
-	\begin{tabular}{rrrrrrr}
-		\hline
-
-	\end{tabular}
-	\caption{\textbf{Summary of data used for MCI analysis}.
-Summary statistics on the number, age, and years of education of individuals used for the analysis.
-Data broken down based on gender and diagnosis.}
-	\label{wave1data}
-\end{table}
-
-<<echo=FALSE, results='asis' >>=
+<<echo=FALSE, results='asis',cache=FALSE >>=
  convert_to_paper_style <- function(x) {
@@
   p_value_table_names <-expand.grid(comparison_strings, col_names)
+  @
+
+<<echo=FALSE, results='asis',cache=FALSE >>=
+  for (region in regions) { 
   p_value_table <- matrix(0,nrow = 7,ncol = 9)
@@
   for (side in sides){
+
+    pooled_test_results = pool_stat_tests_all_regions_sides[side,region][[1]]
     for ( i in 1:7 ) {
@@
   }
-   attr(p_val_table_list, "subheadings") <- paste0("Hemisphere : ",names(p_val_table_list))
-   xtablelist <- xtableList(p_val_table_list)
-  addtorow <- list()
-  addtorow$pos <- list(-1)
-  addtorow$command <- paste0(paste0('& \\multicolumn{3}{c}{', c("KS test","MWU test", "Welch's t-test"), '}', collapse=''), '\\\\')
-  print.xtableList (xtablelist, add.to.row = addtorow, only.contents=FALSE,
+   attr(p_val_table_list, "subheadings") <- paste0("Hemisphere : ",c("Left","Right"))
+   xtablelist <- xtableList(p_val_table_list, caption = paste0("Hypothesis Tests based on pooled LCDM statistics for ",region,collapse= ""))
+   col.names <- c("KS test","MWU test", "Welch's t-test")
+   # Region & \multicolumn{3}{l}{KS test} & \multicolumn{3}{l}{MWU test} & \multicolumn{3}{l}{Welch's t-test}\\
+  rowcom <- list()
+  rowcom$pos = list(-1)
+  rowcom$command = paste0(paste0("Region",paste0(" & \\multicolumn{3}{c}{", col.names , '}', collapse=''),collapse=''), '\\\\')
+  #print(addtorow)
+  print(xtablelist, add.to.row = rowcom, only.contents=FALSE,
     include.rownames=TRUE, sanitize.colnames.function = simp.colnames,
-    type="latex")
+    type="latex",floating.environment = "sidewaystable")
+  }
+
 # create a table of 7 comparisons
@@
 
-\newpage
-\begin{sidewaystable}
-	\centering
-	\footnotesize
-	\begin{tabular}{rr|rrr|rrr|rrr}
-		\hline
-		\multicolumn{2}{c|}{Region} \T\B & \multicolumn{3}{c|}{KS test} & \multicolumn{3}{c|}{MWU test} & \multicolumn{3}{c}{Welch's t-test} \\
-		& & two-sided & less & greater & two-sided & greater & less & two-sided & greater & less \\ \hline
-		& aMCI vs norm\T & $<$.0001 & .0832 & $<$.0001 & $<$.0001 & 1 & $<$.0001 & $<$.0001 & 1 & $<$.0001 \\
-		rh stg & nMCI vs norm & $<$.0001 & $<$.0001 & $<$.0001 & $<$.0001 & 1 & $<$.0001 & $<$.0001 & 1 & $<$.0001 \\
-		& aMCI vs nMCI\T & $<$.0001 & .5210 & $<$.0001 & $<$.0001 & 1 & $<$.0001 & $<$.0001 & 1 & $<$.0001 \\ \hline
-		& aMCI vs norm & $<$.0001 & .9794 & $<$.0001 & $<$.0001 & 1 & $<$.0001 & $<$.0001 & 1 & $<$.0001 \\
-		lh stg & nMCI vs norm & $<$.0001 & .9983 & $<$.0001 & $<$.0001 & 1 & $<$.0001 & $<$.0001 & 1 & $<$.0001 \\
-		& aMCI vs nMCI & $<$.0001 & $<$.0001 & $<$.0001 & .0128 & .0064  & .9936 & $<$.0001 & $<$.0001 & 1 \\ \hline
-		& aMCI vs norm\T & $<$.0001 & $<$.0001 & $<$.0001 & $<$.0001 & 1 & $<$.0001 & $<$.0001 & 1 & $<$.0001 \\
-		rh stg & nMCI vs norm & $<$.0001 & .0121 & $<$.0001 & $<$.0001 & 1 & $<$.0001 & $<$.0001 & 1 & $<$.0001 \\
-		(women)& aMCI vs nMCI & $<$.0001 & $<$.0001 & .0086 & .1065 & .0533 & .9467 & $<$.0001 & $<$.0001 & 1 \\ \hline
-		& aMCI vs norm\T & $<$.0001 & .9989 & $<$.0001 & $<$.0001 & 1 & $<$.0001 & $<$.0001 & 1 & $<$.0001 \\
-		lh stg & nMCI vs norm & $<$.0001 & .9998 & $<$.0001 & $<$.0001 & 1 & $<$.0001 & $<$.0001 & 1 & $<$.0001 \\
-		(women)& aMCI vs nMCI & $<$.0001 & $<$.0001 & .0032 & .0060 & .0030 & .9970 & $<$.0001 & $<$.0001 & 1 \\ \hline
-		& aMCI vs norm\T & $<$.0001 & .0396 & $<$.0001 & $<$.0001 & 1 & $<$.0001 & $<$.0001 & 1 & $<$.0001 \\
-		rh mtg & nMCI vs norm & $<$.0001 & $<$.0001 & $<$.0001 & .5428 & .7286 & .2714 & $<$.0001 & 1 & $<$.0001 \\
-		& aMCI vs nMCI & $<$.0001 & .4099 & $<$.0001 & $<$.0001 & 1 & $<$.0001 & $<$.0001 & 1 & $<$.0001 \\ \hline
-		& aMCI vs norm\T & $<$.0001 & 1 & $<$.0001 & $<$.0001 & 1 & $<$.0001 & $<$.0001 & 1 & $<$.0001 \\
-		lh mtg & nMCI vs norm & $<$.0001 & 1 & $<$.0001 & $<$.0001 & 1  & $<$.0001 & $<$.0001 & 1 & $<$.0001 \\
-		& aMCI vs nMCI & $<$.0001 & .0296 & $<$.0001 & $<$.0001 & 1 & $<$.0001 & $<$.0001 & 1 & $<$.0001 \\ \hline
-		& aMCI vs norm\T &  $<$.0001 & $<$.0001 & $<$.0001 & .5723 & NA & NA & .8289 & NA & NA \\
-		rh itg & nMCI vs norm & $<$.0001 & $<$.0001 & .7620 & $<$.0001 & $<$.0001 & 1 & $<$.0001 & $<$.0001 & 1 \\
-		& aMCI vs nMCI & $<$.0001 & .5502 & $<$.0001 & $<$.0001 & 1 & $<$.0001 & $<$.0001 & 1 & $<$.0001 \\ \hline
-		& aMCI vs norm\T &  $<$.0001 & .8740 & $<$.0001 &  $<$.0001 & 1 & $<$.0001 &  $<$.0001 & 1 & $<$.0001 \\
-		lh itg & nMCI vs norm & $<$.0001 & .7938 & $<$.0001 & $<$.0001 & 1 & $<$.0001 & $<$.0001 & 1 & $<$.0001 \\
-		& aMCI vs nMCI & $<$.0001 & .8740 & $<$.0001 & $<$.0001 & 1 & $<$.0001 & $<$.0001 & 1 & $<$.0001 \\
-	\end{tabular}
-	\caption{\textbf{Temporal Lobe Pooled LCDM Analysis Results.}  Showing p-values obtained from nonparametric distribution tests.}
-	\label{Wave1.TL.nonpara}
-\end{sidewaystable}
-
-\newpage
-\begin{sidewaystable}
-	\centering
-	\footnotesize
-	\begin{tabular}{rr|rrr|rrr|rrr}
-		\hline
-		\multicolumn{2}{c|}{Region} \T\B & \multicolumn{3}{c|}{KS test} & \multicolumn{3}{c|}{MWU test} & \multicolumn{3}{c}{Welch's t-test} \\
-		& & two-sided & less & greater & two-sided & greater & less & two-sided & greater & less \\ \hline
-		& aMCI vs norm\T &  $<$.0001 & $<$.0001 & .9896 &  $<$.0001 & $<$.0001 & 1 &  $<$.0001 & $<$.0001 & 1 \\
-		rh antcing & nMCI vs norm & .0047 & .0024 & .9696 & .0496 & .0248 & .9752 & .0463 & .0232 & .9768 \\
-		& aMCI vs nMCI & $<$.0001 & $<$.0001 & .9986 & $<$.0001 & $<$.0001 & .9986 & $<$.0001 & $<$.0001 & 1 \\ \hline
-		& aMCI vs norm\T & $<$.0001 & $<$.0001 & .8789 & $<$.0001 & $<$.0001 & 1 & $<$.0001 & $<$.0001 & 1 \\
-		lh antcing & nMCI vs norm & $<$.0001 & $<$.0001 & .6552 & $<$.0001 & $<$.0001 & 1 & $<$.0001 & $<$.0001 & 1 \\
-		& aMCI vs nMCI & $<$.0001 & $<$.0001 & .9725 & $<$.0001 & $<$.0001 & 1 & $<$.0001 & $<$.0001 & 1 \\ \hline
-		& aMCI vs norm\T & .0001 & $<$.0001 & .0043 & .2136 & .1068 & .8932 & .5986 & .2993 & .7007 \\
-		rh postcing & nMCI vs norm & $<$.0001 & 1 & $<$.0001 & $<$.0001 & 1 & $<$.0001 & $<$.0001 & 1 & $<$.0001 \\
-		& aMCI vs nMCI & $<$.0001 & $<$.0001 & .9786 & $<$.0001 & $<$.0001 & .9786 & $<$.0001 & $<$.0001 & 1 \\ \hline
-		& aMCI vs norm\T & $<$.0001 & .9911 & $<$.0001 & $<$.0001 & 1 & $<$.0001  & $<$.0001 & 1 & $<$.0001  \\
-		lh postcing & nMCI vs norm & $<$.0001 & .9971 & $<$.0001 & $<$.0001 & 1 & $<$.0001 & $<$.0001 & 1 & $<$.0001 \\
-		& aMCI vs nMCI & $<$.0001 & $<$.0001 & .8553 & $<$.0001 & $<$.0001 & 1 & $<$.0001 & $<$.0001 & 1 \\
-	\end{tabular}
-	\caption{\textbf{Cingulate Gryus Pooled LCDM Analysis Results}   Showing p-values obtained from nonparametric distribution tests.}
-	\label{Wave1.cing.nonpara}
-\end{sidewaystable}
-
 \end{document}

### 2016-11-02 src/ArticleReadyTableGenerate.Rnw
nearly working xtablelist missing double backslashes

@@
     p_value_table <- matrix(0,nrow = 7,ncol = 9)
-  p_val_table_list<-list()
-  xtablelist<- list()
+    p_val_table_list <- list()
+    xtablelist <- list()
     for (side in sides){
@@
       xtablelist[[side]]<-xtab.out
-
     }
@@
     rowcom$pos = list(-1)
-  rowcom$command = paste0(paste0("Region",paste0(" & \\multicolumn{3}{c}{", col.names , '}', collapse=''),collapse=''), '\\\\')
-  #print(addtorow)
-  print(xtablelist, add.to.row = rowcom, only.contents=FALSE,
+    rowcom$command = paste0(paste0("Region",paste0(" & \\\\multicolumn{3}{c}{", col.names , '}', collapse=''),collapse='')," \\\\ " ,collapse="")
+    print(rowcom$command)
+    xtablelist.out<-print(xtablelist, only.contents=FALSE,
       include.rownames=TRUE, sanitize.colnames.function = simp.colnames,
-    type="latex",floating.environment = "sidewaystable")
+      type="latex",floating.environment = "sidewaystable", print.results = FALSE)
+    second_heading <- "(\\\\begin\\{tabular\\}.*)" 
+    xtablelist.out <- gsub( xtablelist.out, pattern = second_heading, perl =  TRUE,fixed=FALSE,
+    replacement =  paste0( "\\1", "\n", rowcom$command, collapse = '') )
+    cat(xtablelist.out,sep="\n")
   }

### 2016-11-03 src/ArticleReadyTableGenerate.Rnw
some cleanup, working multicolumn names for pooled LCDM

@@
 		& \B & & Mean & SD & Mean & SD \\ \hline
-<<Table_1_summarystats, results='asis', eval=TRUE,echo=FALSE,cache=FALSE>>=
+<<Table_1_summarystats, results='asis', eval=TRUE,echo=FALSE,cache=FALSE,message=FALSE,warning=FALSE>>=
   class(summary_table_1.df)<-"data.frame"
@@
 
-<<diag.plot.ICV_1,fig.show='hide',results='asis',echo=FALSE>>=
+<<diag.plot.ICV_1,fig.show='hide',results='asis',echo=FALSE,message=FALSE,warning=FALSE>>=
 #Gender, age, ICV, ED.year, hemisphere
@@
 
-<<subregion_sideway_table_summary_stats,eval=TRUE,echo=FALSE>>=
+<<subregion_sideway_table_summary_stats,eval=TRUE,echo=FALSE,message=FALSE>>=
 #print("subregion_sideway_table_summary_stats")
+
+library(dplyr)
+
 stat.tables.for.regions <- list()
@@
   all.df.lf.stg.lh$aggstat<- as.factor(all.df.lf.stg.lh$aggstat)
+
+  all.df.lf.stg.rh$aggstat<- as.factor(all.df.lf.stg.rh$aggstat)
+
   all.df.lf.stg.lh.grp<- group_by(all.df.lf.stg.lh, aggstat, sex,Diag)
@@
     attr(p_val_table_list, "subheadings") <- paste0("Hemisphere : ",c("Left","Right"))
-    xtablelist <- xtableList(p_val_table_list, caption = paste0("Hypothesis Tests based on pooled LCDM statistics for ",region,collapse= ""))
+    xtablelist <- xtableList(p_val_table_list, caption = paste0("Hypothesis Tests based on pooled LCDM statistics for ",region,collapse= ""),
+                             align = 'l|ccc|ccc|ccc')
     col.names <- c("KS test","MWU test", "Welch's t-test")
+
     # Region & \multicolumn{3}{l}{KS test} & \multicolumn{3}{l}{MWU test} & \multicolumn{3}{l}{Welch's t-test}\\
@@
     rowcom$pos = list(-1)
-    rowcom$command = paste0(paste0("Region",paste0(" & \\\\multicolumn{3}{c}{", col.names , '}', collapse=''),collapse='')," \\\\ " ,collapse="")
-    print(rowcom$command)
+    rowcom$command = paste0(paste0(" Region",paste0(" & \\\\multicolumn{3}{c}{", col.names , '}', collapse=''),collapse=''))
+    #print(rowcom$command)
     xtablelist.out<-print(xtablelist, only.contents=FALSE,
       include.rownames=TRUE, sanitize.colnames.function = simp.colnames,
-      type="latex",floating.environment = "sidewaystable", print.results = FALSE)
-    second_heading <- "(\\\\begin\\{tabular\\}.*)" 
+      type="latex",floating.environment = "sidewaystable", print.results = FALSE,hline.after = c(-1))
+
+    second_heading <- "(\\\\begin\\{tabular\\}.*\\})" 
     xtablelist.out <- gsub( xtablelist.out, pattern = second_heading, perl =  TRUE,fixed=FALSE,
-    replacement =  paste0( "\\1", "\n", rowcom$command, collapse = '') )
+    replacement =  paste0( "\\1", "\n", rowcom$command,' ','\\',' \\ ', collapse = '') )
+    xtablelist.out <- gsub( xtablelist.out, pattern = '\\hline',fixed=TRUE,
+    replacement =  paste0( "\\\\ \\hline", collapse = '') )
+    #print (xtablelist.out)
     cat(xtablelist.out,sep="\n")
